### 2016-11-27 Paper/Paper.tex
paper

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper, 
		   total={170mm,257mm},
		   left=20mm, 
		   top=10mm, 
		   right=20mm, } % or letterpaper (US) or a5paper or....

% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{amssymb}

\usepackage{scrextend}
\changefontsizes[16pt]{13pt}

\usepackage{lipsum}

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

\usepackage{indentfirst} %make section indent

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{RSA Project paper}
\author{\textbf{RSA Group}\\Li Qiu\\Yiwei \\Leester Mei\\Akeem}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\section{Dixon's factorization method}

\section{Quadratic Sieve}

we know Quadratic Sieve is a optimazation of Dixon's method

More text.

\end{document}

### 2016-11-27 RSACracking/src/cracking/SmoothNumberFileParser.java

@@ -10,7 +10,10 @@ import cracking.algorithms.Factorization;
 import cracking.algorithms.LargeGF2Matrix;
 import cracking.algorithms.MathOp;
 import static cracking.algorithms.MathOp.MINUS_ONE;
+import static cracking.algorithms.MathOp.expMod;
 import static cracking.algorithms.MathOp.gcd;
+import static cracking.algorithms.MathOp.modInverse;
+import cracking.algorithms.Primes;
 import cracking.cluster.SmoothInfo;
 import static cracking.utils.Util.error;
 import java.io.FileNotFoundException;
@@ -66,7 +69,7 @@ public class SmoothNumberFileParser {
         relationDupChecker = new HashSet();
         fb = Factorization.fastFactorBase(B, N);
         this.N = N;
-        expMatrix = new LargeGF2Matrix(fb.length+226, fb.length+1, DEFAULT_MATRIX_PATH);
+        expMatrix = new LargeGF2Matrix(fb.length, fb.length+1, DEFAULT_MATRIX_PATH);
         leftOverStack = new HashMap<>();
         parse();
     }
@@ -211,6 +214,7 @@ public class SmoothNumberFileParser {
     public List<BigInteger> calculateFactor(BigInteger N, int[][] nullSpace) {
         BigInteger factorOne = ONE;
         LinkedList results = new LinkedList<>();
+        System.out.println("nullSpace size: " + nullSpace.length);
 //        stream(nullSpace).forEach(row->System.out.println(Arrays.toString(row)));
         for(int i=0, n=nullSpace.length; i<n; i++) {
             BigInteger prodX = ONE;
@@ -253,7 +257,7 @@ public class SmoothNumberFileParser {
         System.out.println();
     }
     
-    private static void saveMatrix(int[][] data, String file) throws IOException {
+    public static void saveMatrix(int[][] data, String file) throws IOException {
         LargeGF2Matrix matrix = new LargeGF2Matrix(data.length, data[0].length, file);
         for(int i=0; i<matrix.getRows(); i++)
             matrix.rowAdd(i, data[i]);
@@ -261,33 +265,41 @@ public class SmoothNumberFileParser {
         
     }
     
+    public static int[][] loadMatrix(String file) throws IOException {
+        int[][] data;
+        try (LargeGF2Matrix matrix = new LargeGF2Matrix(file)) {
+            data = new int[matrix.getRows()][];
+            for(int i=0; i<data.length; i++)
+                data[i] = matrix.getRow(i);
[…]

### 2016-11-27 RSACracking/src/cracking/algorithms/LargeGF2Matrix.java

@@ -208,12 +208,29 @@ public class LargeGF2Matrix implements AutoCloseable {
         return builder.build().toArray(int[][]::new);
     }
     
+    private LinkedList<Integer> getLeftMostOneRows(int column, boolean[] marker) throws IOException {
+        if(column>=C) error("column should be less than %d", C);
+        LinkedList<Integer> result = new LinkedList<>();
+        long startByte = start+column/INTEGER_BITS;
+        file.seek(startByte);
+        int i=0;
+        while(i<R) {
+            byte b = file.readByte();
+            int v = b >> (INTEGER_BITS-column%INTEGER_BITS-1) & 0x1;
+            if(v == 1 && !marker[i]) result.add(i);
+            startByte += colInBytes;
+            i++;
+            file.seek(startByte);
+        }
+        backToStart();
+        return result;
+    }
+    
     public int[][] nullSpace() throws IOException {
         String tempIdentity = "./temp1";
 //        String tempGuassian = "./temp2";
-        int I = Math.max(R, C);
         Stream.Builder<int[]> builder = Stream.builder();
-        LargeGF2Matrix identity = new LargeGF2Matrix(I, I, tempIdentity);
+        LargeGF2Matrix identity = new LargeGF2Matrix(R, R, tempIdentity);
         identity.identity();
 //        LargeGF2Matrix gaussian = new LargeGF2Matrix(R, C, tempGuassian);
 //        int newRow = 0;
@@ -221,11 +238,7 @@ public class LargeGF2Matrix implements AutoCloseable {
         int onePercent = C/100;
         for(int c=0; c<C; c++) {
             if(onePercent!=0 && c % onePercent == 0) System.out.printf("calculate matrix: %d percent \n", c/onePercent);
-            int[] col = getColumn(c);
-            LinkedList<Integer> rows = new LinkedList<>();
-            for(int j=0; j<R; j++) {
-                if(col[j]==1 && !marker[j]) rows.add(j);
-            }
+            LinkedList<Integer> rows = getLeftMostOneRows(c, marker);
             if(rows.isEmpty()) continue;
             int pivot = rows.poll();
             marker[pivot] = true;

### 2016-11-27 RSACracking/src/cracking/algorithms/Primes.java

@@ -15,6 +15,7 @@ import static cracking.utils.Util.randomBigInteger;
 import java.math.BigInteger;
 import static java.math.BigInteger.ONE;
 import static java.math.BigInteger.ZERO;
+import static java.math.BigInteger.valueOf;
 import java.util.Arrays;
 import java.util.HashMap;
 import java.util.Iterator;
@@ -211,6 +212,16 @@ public class Primes {
         }
     }
     
+    public static BigInteger eulerTotient(BigInteger n, BigInteger[] factors) {
+        BigInteger ret = n;
+        BigInteger tmp = ONE;
+        for(BigInteger p : factors) {
+            tmp = tmp.multiply(p.subtract(ONE));
+            ret = ret.divide(p);
+        }
+        return tmp.multiply(ret);
+    }
+    
     public static int[] eratosthenesSieve(int n) {
         int[] sieve = new int[n+1];
         Arrays.fill(sieve, 0);
@@ -303,8 +314,8 @@ public class Primes {
     
     public static void main(String[] args) {
         RandomPrimeGenerator randomGen = new RandomPrimeGenerator();
-        BigInteger b1 = randomGen.gen(87).next();
-        BigInteger b2 = randomGen.gen(85).next();
+        BigInteger b1 = randomGen.gen(60).next();
+        BigInteger b2 = randomGen.gen(69).next();
         System.out.println(b1);
         System.out.println(b2);
         BigInteger N = b1.multiply(b2);

### 2016-11-27 RSACracking/src/cracking/algorithms/QuadraticSieve.java

@@ -268,11 +268,11 @@ public class QuadraticSieve implements Runnable {
     public static void main(String[] args) throws FileNotFoundException, IOException {
         
 //        BigInteger N1 = Main.TARGET; //new BigInteger("6275815110957813119593022531213");
-//        BigInteger N1 = new BigInteger("2903978063470729867275975450010365349829284825411351");
-        BigInteger N1 = new BigInteger("13290059"); //new BigInteger("6275815110957813119593022531213");
-        int B = 100;
-        QuadraticSieve sieve = new QuadraticSieve(N1, B, 450);
-        System.out.println(Arrays.toString(Factorization.fastFactorBase(B, N1)));
+        BigInteger N1 = new BigInteger("489293762578746481445307920902864380533");
+//        BigInteger N1 = new BigInteger("6275815110957813119593022531213"); //new BigInteger("13290059");
+        int B = 150_000;
+        QuadraticSieve sieve = new QuadraticSieve(N1, B, 80_000_000);
+//        System.out.println(Arrays.toString(Factorization.fastFactorBase(B, N1)));
         Set<SmoothInfo> relations = new HashSet<>();
         sieve.setBSmoothRef(relations);
         sieve.run();

### 2016-11-27 Paper/Paper.tex
My paper

@@
 
-\section{Dixon's factorization method}
-
 \section{Quadratic Sieve}
 
-we know Quadratic Sieve is a optimazation of Dixon's method
+Quadratic Sieve method is actually discovered step by step.
+It is a optimization of Dixon's Factorization Method.
+So, to learn what is Quadratic Sieve, we have to understand Dixon's Method.
+And Dixon's Method is also related to Fermat's Factorization and Kraitchik's Factorization Method.
+Here, I will briefly introduce these three factorization methods.
 
-More text.
+\subsection {Brief Hierarchies Of Quadratic Sieve}
 
+\subsubsection {Fermat's Factorization}
+Fermat factorization method is very straight forward, if we are going to factor $n$, since: $$n = ab \Rightarrow \left [\frac{1}{2}(a+b) \right ]^{2} - \left [\frac{1}{2}(a-b) \right ]^{2}$$
+
+let $$ x= \frac{1}{2}(a+b),\ y= \frac{1}{2}(a-b) \Rightarrow n = x^2 - y^2$$
+
+Therefore, we just need to find a $x$ satisfy: $$Q(x) = y^2 = x^2 - n$$
+
+and obviously, the smallest $x$ is $\lceil \sqrt[2]{n}\rceil$ and if we can find a $Q(x)$ is a square root, then we can find the factors of $n$ which is $a=x+y, b=x-y$
+
+\subsubsection {Kraitchik's Factorization}
+Kraitchik's method is instead of checking $x^2-n$ is a square, he suggests to check $x^2 - kn$ a square number, which is equivalent to find $y^2 \equiv x^2 \pmod{n} $.
+And the only interesting solution is $ x \not\equiv \pm y \pmod{n}$.
+Besides this, instead of seeking one $x^2-n$ is square, he was looking for a set of number $ \{x_1, x_2, \dots, x_k\} $ such that $\displaystyle y^2 \equiv \prod_{i=1}^k{(x_i^2 - n)} \equiv \prod_{i=1}^k{x_i^2} \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n} $ is square.
+if he can find a relation like this, then, the factors of n is $\displaystyle gcd(|y \pm \prod_{i=1}^k{x_i}|, n)$
+
+\subsubsection {Dixon's Factorization}
+One of the great improvement of Dixon's method comparing to the method before is that he replace the requirement from ``is a square of an integer'' to ``has only small prime factors''.
+To explain this we need introduce 2 concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.
+
+\textbf{Factor Base} is a set of prime factors $S_{fb}=\{p | p \le B\}$ where $B$ is some integer.
+
+\textbf{Smooth Number} is a integer that all its prime factor within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$.
+We called Q is a \textbf{B-Smooth} Number.
+
+Recall Kraitchik's Method, he suggests to find a relation $y^2 \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n}$.
+But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$.
+For each relation is found, it can represent as a exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$.
+And searching the null space of this matrix, could help us to find the square integer.
+Since $M\vec{v} = 0$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to 0, which also implies the products of corresponding Q to that row is a square integer.
+After found the relation, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$
+
+\subsection {Math and Algorithm in Quadratic Sieve}
+
+\subsubsection{Legendre Symbol \& Quadratic Reciprocity}
+
+\subsubsection{Shanks Tonelli's Algorithm}
+
+\subsubsection{Logarithm Approximation}
+
+\subsection {Sieving In Quadratic Sieve}
+
+\subsubsection {How we do it}
+
+\subsection {16 mins to less than 1s}
 \end{document}

### 2016-11-28 Paper/Paper.tex
paper
update paper

@@
 
+\newcommand{\legendre}[2]{\left(\frac{#1}{#2}\right)}
 %%% END Article customizations
@@
 
-\subsubsection{Legendre Symbol \& Quadratic Reciprocity}
+\subsubsection{Legendre Symbol \& Laws of Quadratic Reciprocity}
+
+From now, we know two ways to test whether $n$ is a quadratic residue mod p, one is Euler Criterion, and the other is Legendre symbol.
+In practice, probably because we factor base is not insanely large, we did not noticed how much faster does Legendre symbol than the Euler criterion (since Euler criterion is an $\mathcal{O}(\log{n}) $ algorithm).
 
@@
 
+Shanks Tonelli's Algorithm is a faster algorithm to find the root of a quadratic residue.
+In class, we only learn the simple case, which is when $p \equiv 3 \pmod{4}$.
+Since this algorithm is very important for quadratic sieve, we are going to prove the algorithm.
+
+Given $x^2 \equiv n \pmod{p} $, we want to find x.
+
+let $p-1 = 2^eS,\ x \equiv n^{\frac{S+1}{2}} \pmod{p},\ t \equiv n^S \pmod{p}.$
+
+we have, $x^2 \equiv n^{S+1} \equiv n^Sn \equiv tn \pmod{p}$, notice that,
+
+if $t \equiv 1 \pmod{p},$ our $x = \pm n^{\frac{S+1}{2}} \pmod{p}$
+
+if $t \not\equiv 1 \pmod{p}$, then find a quadratic non-residue $a$ and let $b \equiv a^S \pmod{p}$, then, $b^{2^e} \equiv (a^S)^{2^e} \equiv a^{2^eS} \equiv a^{p-1} \equiv 1 \pmod{p}$, Since we know $a$ is a quadratic non-residue, By Euler Criterion, $a^{\frac{p-1}{2}} \equiv b^{2^{e-1}} \equiv -1 \pmod{p} \rightarrow 2^e$ is the order of b.
+
+we have $t^{2^e} \equiv 1 \pmod{p}$, and we let $2^{e^\prime}$ be the order of $t \pmod{p}$, since $n$ is a quadratic residue, $e^\prime \le e-1$
+
+let $c \equiv b^{2^{e-e^\prime-1}} \pmod{p}$, $b^\prime \equiv c^2$, $t^\prime = tb^\prime$, $x^\prime = cx$, after this construction, $x^{\prime 2} \equiv t^\prime n \pmod{p}$ still holds, since $x^{\prime 2} \equiv b^{2^{e-e^\prime}}x^2 \equiv tnb^{2^{e-e^\prime}} \equiv tnb^\prime \equiv  t^\prime n \pmod{p}$.
+And we can repeat this process until $e^\prime = 0$ we can find a $t^\prime = 1$, and our final solution is $ \pm x^\prime \pmod{p}$
+
 \subsubsection{Logarithm Approximation}
+
+Logarithm approximation plays a very import role in implementing the sieving process.
+Since we use the polynomial $Q(x) = (x)^2-n$, and we want to sieving in the interval  $[\lfloor \sqrt{n} \rfloor - M, \lfloor \sqrt{n} \rfloor + M]$, therefore, $\log{(Q(x))} \approx \log{(Q(\lfloor \sqrt{n} \rfloor + M))} = \log{(2M\sqrt{n}+M^2)}$, because of $M^2$ is trivial if $\sqrt{n}$ is huge, $\log{(Q(x))} \approx 0.5\log{n} + log{M}$.
+We also know $Q(x) = \prod_{i=1}^k{p_i^{a_i}}$ where $p_i \in S_{fb}, k=|S_{fb}|$ if $Q(x)$ has a smooth relationship in our factor base, then we have,  $\log{(Q(x))} = \log{\prod_{i=1}^k{p_i^{a_i}}} = \sum_{i=1}^k{a_i\log{p_i}}$.
+This formula tell us if we can find a $\log{Q(x)} = \sum_{i=1}^k{a_i\log{p_i}} \approx 0.5\log{n} + log{M}$ it probably a candidates of smooth number.
 
@@
 
-\subsubsection {How we do it}
+\subsubsection {Pre-Sieving}
 
-\subsection {16 mins to less than 1s}
+\subsubsection {Sieving}
+
+\subsubsection {Saving the result}
+
+\subsubsection {Our optimization}
+
+\subsection {Linear Algebra (Finding Null Space) }
+
+\subsection {Problems we met, and solutions}
+
 \end{document}

### 2016-11-28 Paper/Paper.tex
update paper

@@
 \usepackage{indentfirst} %make section indent
+
+%\usepackage{tikz} %drawings
 
@@
 
+Quadratic Sieve's sieving method is inspired by the ancient Eratosthenes Sieve.
+The Eratosthenes sieve is to crossing out the multiples of prime, and the leftovers are the candidates of prime.
+In quadratic sieve, we want a relation $x^2 \equiv n \equiv r \pmod{p}$ where $r < p$, in order to keep this relation, we marking the multiples of $p$ plus $r$ as our candidates.
+
 \subsubsection {Pre-Sieving}
+
+Before sieving we need to build our factor base, and in order to build our factor base, we need to choose a number $B$ which all the prime in our factor base must less than or equal to $B$.
+If $B$ is too small, it will be very hard to find such smooth relations, but if $B$ is too large, we will be facing a huge matrix and finding the null space of it will be very time consuming.
+And our $B$ choice is one million (we will explain why later).
+After choose $B$, we have another criteria for our factor base, that is the prime factor $p$ in our factor base must make our N(the number we want to factorize) to be a quadratic residue.
 
@@
 
+For each prime factor in factor base, we use shank-tonelli's algorithm to find the roots(which means the x) of $x^2 \equiv N \pmod{p}$, if $p = 2$, the root can only be 1, and for every other odd prime factor we have two roots which is $x$ and $p-x$, we save the position of $x+i*p$ and $p-x+i*p$ where $i \in \{0, 1, \dots \}$ until $x+i*p>M$ where $M$ is our bound of searching space.
+And at the meantime, accumulate $\log{p}$ to the position in our sieve array.
+
 \subsubsection {Saving the result}
 
-\subsubsection {Our optimization}
+During the sieving stage, when we found a position and it's value in our sieve array is close to $0.5\log{n} + log{M}$ we consider it is our smooth candidate.
+But to define what is close to, we need a threshold.
+To determine value of the threshold little articles we read mentioned about it, some of articles said that the value of this threshold is a small error.
+We made a bunch of tests, and we found when the threshold is less than 8 it seems accurate(we will explain the detail of the tests later).
+And we also found that the threshold is good to be small, because we do not need find all the smooth relations in this range, we just need to find the relation as fast as possible.
+Since if the threshold is large, we need to double check the relation, but if the threshold is small, we do not have to.
 
-\subsection {Linear Algebra (Finding Null Space) }
+\subsection {Linear Algebra In Quadratic Sieve}
 
-\subsection {Problems we met, and solutions}
+If we use logarithm approximation, it is very likely to find partial relations instead of full relation.
+A full relation means the relation is exactly the smooth number.
+A partial relation means that there are factors out of our factor base.
+A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which have the leftover in common, the leftover will be canceled.
+In other words, if we can find two partial relations have the same leftover factors we can treat them as two full relations.
 
+After we collecting enough relations, we use them to create a exponent matrix.
+The common way to do this, is use trial division.
+For each relation we divide out all its  prime factor in the factor base, and use the powers mod 2 to build a exponent vector.
+Then, if we can find $k$ relations where $k = |S_{fb}|$, we have k exponent vectors to form a exponent matrix.
+
+Since in our approach, $|S_{fb}|\approx 40000$, we can simply use Gaussian elimination to find null space.
+But for larger matrix, something like 100000x100000 it is better to use Block Lanczos algorithm.
+By the way, the Meataxe is using Gaussian Elimination to find null space as well.
+
+\subsection {Details of Our implementation \& optimization}
+
+\renewcommand\labelenumi{\Roman{enumi}}
+\begin{enumerate}
+\item \textit{Choosing B:} 
+\end{enumerate}
+
+\subsection {Problems we met \& the solutions}
+
+\subsection {Tables and Graphs of Experiments}
 \end{document}

### 2016-11-28 RSACracking/src/cracking/algorithms/Factorization.java
update paper

@@ -6,6 +6,7 @@
 
 package cracking.algorithms;
 
+import cracking.Main;
 import static cracking.algorithms.MathOp.MINUS_ONE;
 import static cracking.algorithms.MathOp.TWO;
 import static cracking.algorithms.MathOp.expMod;
@@ -244,6 +245,8 @@ public class Factorization {
 
         
         BigInteger N = new BigInteger("6275815110957813119593022531213");        
+        int[] fb = Factorization.fastFactorBase(1398139, Main.TARGET);
+        System.out.println(fb.length);
 //        BigInteger smooth = valueOf(2505157706368382L).pow(2).subtract(N);
 //        List<BigInteger> fb = Factorization.factorBase(valueOf(15000), N);
 //        Map<BigInteger, Integer> factors = new HashMap<>();

### 2016-11-28 RSACracking/src/cracking/algorithms/LargeGF2Matrix.java

@@ -27,7 +27,7 @@ import java.util.stream.Stream;
  */
 public class LargeGF2Matrix implements AutoCloseable {
 
-    private static final int INTEGER_BITS = 8;
+    private static final int BYTE_BITS = 8;
     
     private final int R;
     private final int C;
@@ -37,15 +37,15 @@ public class LargeGF2Matrix implements AutoCloseable {
     private final RandomAccessFile file;
     
     private static int getPad(int row) {
-        return INTEGER_BITS-row%INTEGER_BITS;
+        return BYTE_BITS-row%BYTE_BITS;
     }
     
     public static byte[] intArrayToRow(int[] array) {
         int[] gf2 = stream(array).map(i->i%2).toArray();
         ByteArrayOutputStream bytesStream = new ByteArrayOutputStream();
-        for(int i=0, l=gf2.length; i<l; i+=INTEGER_BITS) {
+        for(int i=0, l=gf2.length; i<l; i+=BYTE_BITS) {
             byte compress = (byte)0;
-            int limit = INTEGER_BITS;
+            int limit = BYTE_BITS;
             int j = i;
             while(--limit >= 0) {
                 if(j >= l) break;
@@ -60,8 +60,8 @@ public class LargeGF2Matrix implements AutoCloseable {
         int[] intArray = new int[colSize];
         for(int i=0; i<row.length; i++) {
             byte compressed = row[i];
-            int limit = INTEGER_BITS;
-            int j = i*INTEGER_BITS;
+            int limit = BYTE_BITS;
+            int j = i*BYTE_BITS;
             while(--limit >= 0) {
                 if(j >= colSize) break;
                 intArray[j++] = compressed >> limit & 1;
@@ -81,7 +81,7 @@ public class LargeGF2Matrix implements AutoCloseable {
         file.writeInt(R);
         file.writeInt(C);
         start = file.getFilePointer();
-        colInBytes = (C+pad)/INTEGER_BITS;
+        colInBytes = (C+pad)/BYTE_BITS;
         initializeZero();
     }
 
@@ -90,17 +90,17 @@ public class LargeGF2Matrix implements AutoCloseable {
         R = file.readInt();
         C = file.readInt();
         pad = getPad(C);
-        colInBytes = (C+pad)/INTEGER_BITS;
+        colInBytes = (C+pad)/BYTE_BITS;
         start = file.getFilePointer();
     }
     
     public void add(int v, int r, int c) throws IOException {
[…]

### 2016-11-28 Paper/Paper.tex
paper update

@@
 \begin{enumerate}
-\item \textit{Choosing B:} 
+\item \textit{Choosing B \& M:} \vspace{2mm}
+\\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}.
+At first in class professor emphasis that the number is just a toy number, therefore, we are using the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$.
+And then, we use  this bound to test our number, the result is 1.4 million and the factor base size is about 50 thousands.
+But we use pollard rho found a small factor, and we reduce the original number by dividing this factor which is 809.
+And we calculate again it became 970000+, and our factor base is shrink to 40 thousands.
+For the convenience of communication, we choose 1 million as our B.
+
+For choosing M, we do not really know any formulas or suggestions from the resources we read.
+Our M is just based our experiments.
+Our main idea is to set M is large enough, and we continuously searching until, we found enough relations.
+In our experiment we set M to 2 trillion, which means we are searching 4 trillion numbers.
+
+\item \textit{Building Factor Base:} \vspace{2mm}
+\\ To build the factor base, first we need to generate primes.
+There are several ways to do it.
+Our approach build a prime generator by Eratosthenes Sieve.
+we used a dictionary to dynamically hold the relations.
+For example, if a test number, is not in the dictionary then it is a prime, and then add the square of this number to the dictionary.
+if the test number in the dictionary, then, pull out all its factors and add the sum of the test number and its factor to the dictionary.
+after that, delete the test number from the dictionary.
+Then, we use this generator to build our factor base, if the prime build by generator satisfy two conditions which are less than $B$ and makes $N$ be the quadratic residue, then add it to our factor base, otherwise, continue generating until the prime greater than our $B$.
+The good part of this method is that the building process is very fast, the cons is that it use extra memory to save the relations.
+
+To decide whether $\legendre{N}{p} = 1$, we implemented both Euler criterion and Legendre Symbol.
+And probably because our factor base was not enough, we did not notice Legendre Symbol is much faster than Euler Criterion.
+Since professor suggest us use Legendre Symbol, we are using Legendre symbol to test $\legendre{N}{p}$.
+
+\item \textit{Pre-Sieving:} \vspace{2mm}
+\\ In this stage, we did a lot optimizations.
+First, we use array as dictionary, which means we use prime value as array's index, since our B is one million, our array length is one million.
+The reason why we do this is we need extremely fast in our sieving process, since array get operation is $\mathcal{O}(1)$.
+And the downside is obviously wasting memory.
+Then, we use this approach to save 3 informations.
+First one, is the roots of quadratic residue.
+Since every odd prime has two solutions, we use a two dimension array to save both.
+And we also cache the value of $\log p$, Since we do not want any unnecessary calculations in our sieving process.
+And finally, we also store the offset of x from the start position $\lfloor \sqrt{N} \rfloor - M$, i did not see any resources mentioned this, but we think it is useful, since we can very easily obtain the smooth number by just add offset to start position.
+
+And here is a story about how math help us solve problems.
+As we motioned before, we want save the info of the offset of x from the start position, which is also find the closest position from x that satisfy $x+o \equiv r \pmod{p}$ where $x$ is start position $o$ is offset, and $r$ is the square roots of quadratic residue.
+And we want find $o$, at very first we use a very naive way to do it, since $x+o=r+ip$ where $i \in \{0,1,\dots\}$ we just keep increasing i until we found a value makes two side equal.
+And then we found this approach was very slow when the factor base is getting bigger (we used to choose a much smaller factor base).
+Then, we just sit down and wrote down the formula and analysis.
+And we realize if we want the $o$, it is just simply $o = r-x \pmod{p}$.
+After we use this new approach the program runs 2 times faster than before.
+Then we think, do a math analysis before writing code is probably a good idea.
+
+\item \textit{Sieving:} \vspace{2mm}
+\\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$].
+Therefore, its length is $2M+1$.
+The sieving process is just go through each prime in our factor base.
+Get its position which already cached in previous stage, and add $r+ip$ where $r$ is the position to the sieve array.
+
+This stage is probably most simple part of our program.
+It is not the idea is simple, it is made to be simple, since this is the bottle neck of our whole program.
+if we made this process calculates more, the program will slow down dramatically.
+And we also did this part in parallel.
+Not only multi-thread but also multi-process.
+
+We implemented a sever which only responsible to generate job which specify the range to search and add it to a task queue.
+And then, each client connected to sever and got job from the queue.
+The job could be very large, so we split the job according to the memory of client, and starting multi-thread according to the number of processors of client, and sieving.
+
+\item \textit{Save Sieving Result:}
+\item \textit{Build Exponent Matrix:}
+\item \textit{Finding Null Space:}
+\item \textit{Calculating Factors:}
+
 \end{enumerate}
 
-\subsection {Problems we met \& the solutions}
+\subsection {Results of Experiments}
 
-\subsection {Tables and Graphs of Experiments}
+\pagebreak
+\begin{thebibliography}{99}
+
+\bibitem{contini} Scott Patrick Contini, [\textit{Factoring Integers with the Self-Initializing Quadratic Sieve}], 1997
+
+\end{thebibliography}
+
 \end{document}

### 2016-11-29 Paper/Paper.tex
paper updates

@@
 \usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{mathtools}
 
@@
 
+\newcommand{\itemgap}[1][2]{\vspace{#1mm}}
 \newcommand{\legendre}[2]{\left(\frac{#1}{#2}\right)}
@@
 
-\title{RSA Project paper}
+\title{RSA Project Report Paper}
 \author{\textbf{RSA Group}\\Li Qiu\\Yiwei \\Leester Mei\\Akeem}
@@
 
+\section{Introduction}
+For this assignment, we were given the task of breaking RSA encryption.
+The data we were given is simply the public key, and the cipher modulus.
+The problem has specified that the message was encrypted to number format by each being equal to a set of one or two number (Ex: A = 1,B = 2,with Z = 26).
+
+We have the public exponent $ e = 31 $.The public modulus $N=$  49596093737736060492038360\\5744987602701101399399359259262820733407167.
+And the cipher text, 19705178523446373241\\426321455642097240677633038639787310457022491789, giving us the full public mechanism in the form $ C \equiv M^{e} $ (mod N)
+
+\indent This is all the information afforded to us to solve the problem of recovering the message.
+Now we will discuss potential attacks against RSA and the pitfalls of many of them given the information provided.
+
+\subsection{ Common Modulus Attack}
+		Assume the same common modulus N is used by all the users under a system, so each user i gets a unique public key pair $<N,e_i>$ and a unique private key pair $<N,d_i>$ from the central system.
+		Now, Alice is sending an encrypted message C = $M^{e_{Alice}}$ mod N to Bob (Bob has to know either factors of N or to do the same thing with Eva). 
+		However, another user Eve can also get Alice's original message by using her own keys, ${e_{Eve}}$ and ${d_{Eve}}$, to factor common modulus N. There are many ways to factor N if we know e and d.
+		For example, we can guess $\phi(n)$  from ed = 1 (mod $\phi(n)$).
+Since ed -1 = k$\phi(n)$ = k$2^x$r (because $\phi(n)$ must be an even number, $\phi(n)$ can be expressed in powers of 2 times an odd number with a certain integer k),
+		we can get correct $\phi(n)$ in $\log_2(N)$.
+		Or if we are lucky enough that N = pq, $\phi(n)$ = (p-1)(q-1) = pq - (p+q) +1 = n - (p+q) +1.
+Then q = (n- $\phi(n)$ +1)-p.
+By Substituting q into N =pq, N = p(n- $\phi(n)$ +1)-p), which is equal to $p^2$ - p(n-$/phi(n)$+1)+n =0.
+		Now we can factor N by solving this quadratic equation.
+
+		After Eve knows the factors of N, she can compute $\phi(N)$ and compute ${d_{Alice}}$ ${e_{Alice}}$ = 1 mod $\phi(N)$ to find ${d_{Alice}}$ by Euclidean algorithm (since ${e_{Alice}}$ is public information).
+		Then Eve can recover Alice's M = $C^{d_{Alice}}$ mod N.
+		Therefore, common modulus N is not secure.
+
+		However, we are only given one public key $<N,e>$ and there are no other users involving in our case. So, this attack does not apply to our case. 
+\subsection{Blinding Attack on RSA signature}
+		Assume Alice has a public key pair $<N,e>$ and a private key pair $<N,d>$.
+Eve asks for Alice to sign a random message M' (M' = $r^eM$ with r picked by Eve randomly and M is the targeted high secret message).
+		Then, by the fact that signature S' = $M'^d$ mod N and S = s'/r, Eve can recover M by computing $S'^e/r^e$ since $S^e$ = $(S')^e/r^e$ = $(M')^ed / r^e$ = $M'/r^e$ = M mod N.
+
+		Our problem doesn't involve in digital signature.
+\subsection{Small private Exponent Attack}
+
+		1. d has to be large enough to be secure (drawback: large d would take more computation time and a large storage space for smart cards)
+
+		2. d can be recovered in linear time if d is small
+		it does not apply to our case because we don't have information about d so that it would be inefficient to apply this attack.
+
+\subsection{ Small public Exponent Attack}
+		Sometimes it is possible that we use small small public exponent in order to reduce encryption time.
+However, it is not secure and we show several methods to break RSA by having small public exponent as following.
+
+\subsubsection{Hastad's Broadcast Attack}
+		Assume Alice wants to send a message to many users (k of them). It is possible that Alice is lazy to compute $M^(e_i)$ according to each user, so she may choose the same e for all users.
+		Then She first encrypts the message M according to a user's public key pair $<N_i, e>$ by $M^e$ (mod $N_i$) = $C_i$ and sends the cipher text $C_i$ to the corresponding user i. 
+		If Eve can intercept k cipher text, she can recover the encrypted message as following.
+		She first take congruence of each user's cipher text to get $(M_i)^k$ by $C_i$ = $(M_i)^k$ (mod $N_i$).
+Then she applies the Chinese Remainder Theorem to each $C_i$, which gives C' = $M^k$ (mod ($N_1$)*($N_2$)*...*($N_k$)).
+		Since M is less than all $N_i$, $M^k$ < ($N_1$)*($N_2$)*...*($N_k$) is satisfied, which means C' = $M^k$. So, Eve can recover M by taking k root of C'.
+		This attack is efficient only when e is the same for all users and e is small.
+
+		It does not apply to our case because it has to send message to many people.
+In our case, Alice only send message to Bob so we only have one public key pair $<N, e>$.
+Thus, we cannot recover M by using Chinese Remainder Theorem.
+
+\subsubsection{Franklin-Reiter Related Message Attack}
+
+		it does not apply to our case because it has to send related messages using same modulus N. In our case, we only intercept one message.
+
+\subsection{implementation attacks}
+	it does not apply to our case because it needs to measure the time it takes for decryption. In our case, we do not have such information.
+
+\section{Factoring Attacks Against RSA}
+\subsection{Special Factoring Methods}
+		The efficiency of this type of methods usually depends on the size of the first prime factor or some special form of N.
+If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fast.
+		Thus, we usually apply these special factoring methods to find whether there is a small prime factor to divide N so that we can decrease the size of N before proceed with the general factoring methods.
+
+ \subsubsection{ Brute Force}
+		The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increase by 2.
+		In this month, we search up to 58248674129 (35-bit), which is 21 digits difference with the second prime factor 64820903298591432157114065708311(105-bit).
+		And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search.
+		Moreover, the completely search from 1 to N will take about 5*$10^{55}$ years. (all the calculations above are done by Java) 
+		Therefore, if we only use brute force search to factor N, we won't be able to reach the solution until 7.6*$10^{16}$ generations after (and each generation should continue this task non-stop).
+
+ \subsubsection{Pollard's Rho method}
+		Assume we want to factor a positive number N. We begin by randomly selecting with replacement from the set $S_1$ = {0,1,2,...,N-1} to form a sequence $x_1$, $x_2$, $x_3$,.... 
+		Define $x_i$' = $x_i$ mod p so that our sequence is now $x_1$', $x_2$',$x_3$',... with each $x_i$' belongs to $S_2$ = {0,1,2,...,p-1}.
+		Because the sets $S_1$,$S_2$ are finite, eventually there will be a repeated integer in both sequence.
+Say, $x_i$' = $x_j$' for i $\ne$ j.
+Then, $x_i$ $\equiv$ $x_j$ mod p, which means p$|$($x_i$ - $x_j$) if $x_i$ is not equal to $x_j$.
+		So, gcd($|$$x_i$ - $x_j$$|$, N) $\ne$ 1. Then if, gcd($|$$x_i$ - $x_j$$|$, N) $\ne$ N, we have found a proper divisor for N.
+
+		In our case, we factor 495960937377360604920383605744987602701101399399359259262820\\733407167 = 809*613054310726032886180943888436325837702226698886723435429939101863 using Pollard's rho algorithm within 6 ms by Java.
+		And after using Miller-Rabin's primality test, we found that 613054310726032886180943888436325837702226698886723435429939101863 is a composite number.
+		So, we keep factoring 61305431072603288618094388843632583770222669888\\672435429939101863 using Pollard's rho algorithm.
+		However, the Pollard's rho algorithm program is still running, so we failed to use this algorithm to factor N in one month.
+\subsubsection{Pollard's P-1}
+By Fermat’s Little Theorem, if $a$ and $p$ are coprime, then $a^{p-1} = 1(mod\ p)$, which means that $a^{k(p-1)} (mod\ p)$ should also be $1$.
+Say $p$ and $q$ are prime factors of the number we want to factor, $N$.
+If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L-1}$.
+From there we can calculate gcd($a^{L-1}$, $N$), which we can have two cases.
+The first case is if the gcd($a^{L-1}$, $N$) is not equal to $N$, which means that the gcd must be our prime factor p (since $a^{L-1} = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$).
+The second case is if gcd($a^{L-1}$, $N$) = $N$, which implies that $N| a^{L-1}$.
+In this case $q$ will also divide $a^{L-1}$, meaning $a^{L} = 1(mod q)$ (because $a^{L-1} = 0(mod q)$).
+\\\\Algorithm
+	\\1. Choose $a$, where $1<a<n$
+	\\2. Check if gcd($a$,$n$) != 1, if it is, (though not likely), then you’ve found a factor, $a$.
+	\\3. Otherwise, for $r$ = $2,3,..$ compute the gcd($a^{r!-1}$, $n$) = $d$:
+	\\If $d = n$, then go back to (1), try a different a
+	\\If $d \ne n$, but $d > 1$,  then $d$ is a prime factor of 
+	\\Otherwise, if $d = 1$, increment $r$ and repeat
+\\\\
+Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$, and take the product of all primes < $B$ as well, with an increasing $B$ instead of $r!$.
+The goal is to find an $L$ such that it is a large multiple of $p-1$
+\\\\An attempt at factoring our $N$ using Pollard’s $p-1$ factoring algorithm also proved to yield similar results with Pollard rho factorization.
+The algorithm itself, which relies on $p-1$, where $p$ is a prime factor of $N$ containing a lot of small prime factors, fails to further factor $N$ beyond the initial 809 factor.
+
+\subsection{William's P+1}
+Now we will be discussing our attempt at factoring our modulus using the Williams P+1 method of factoring.
+This method was based on one of the steps in the P-1 algorithm, and it's effectiveness is determinant on whether p+1 where p is a prime divisor of the number to be factored is a smooth number (Smooth numbers will be discussed in-depth in the section about the quadratic sieve).
+For this section the explanation of the method will come primarily from Williams paper from 1982 "A P+1 Method of Factoring" and then a discussion of the implementation and the result of this method against both the project modulus and the modulus with 809 factored out.
+
+\indent As stated earlier the P+1 method is based on one of the steps of the P-1 algorithm.
+The specific step that is talked about is the first step of the algorithm.
+The specific step will be William's referred to will be reiterated here drawn mostly from his 1982 paper.
+Let a prime factor of a composite number N have the property that $p = (\prod^{k}_{i=1}q^{a_i})+1$ where $q_i$ is the ith prime and $q^{\alpha_i}_i\leq B_i$.
+$q^{\beta}_i$ will now be a power of $q_i$  with $q^{\beta}_i \leq B_1$ and $q^{\beta+1}_i > B_1$.
+Now we allow a value R to be defined as $R= \prod^{k}_{i=1}q^{\beta _i}_i$.
+With this in mind a few additional facts appear.
+Firstly $p-1|R$ and due Fermat's Little Theorem  $a^{p-1} \equiv 1$ (mod p) and $a^{R} \equiv 1$ (mod p) when a is a constant which is co-prime to N.
+The result of these statements is that $p|(N,a^{R}-1)$.
+This step is the basis of the P+1 method, which utilizes Lucas functions.
+
+\indent A Lucas sequence is a recurrence relation that satisfies of $x^2 - Px+Q$ where with P and Q being integers.In the paper there are seven different identities for Lucas sequences described.These identities stem from this first equation (which is noted by the paper to be the formal definition of a Lucas Sequence)  $U_n(P,Q) = (\alpha^{n}-\beta^{n})/(\alpha-\beta), V_n(P,Q) = \alpha^{n}+\beta^{n}$ where $\alpha$ and $\beta$  are the roots of $x^{}2 - Px+Q$.
+All the identities won't be outlined here, however there are multiple identities used in the algorithm for the P+1 method.
+\\\\
+\indent The algorithm itself as outlined in the paper is similar to the following.
+Let $p = (\prod^{k}_{i=1}q^{\alpha_i}_i - 1)$ where p is a prime factor of N.
+If we define R in the same way as in the P-1 method then $p+1|R$ and $p|U_R(P,Q)$ thus $p|(U_R(P,Q),N)$.
+The issues with this method is the calculation of $U_R$ which can be a very large number as the size of R may be very large.
+A method is described to get around this which ends in an assumption that Q may be set to be equal to one in the calculations of all Lucas sequences involved in this algorithm.
+\\\\
+\indent There is a second bypass involved to decrease the computational load that leads to the primary implementation done for our assignment.
+The details to this implementation are outlined in the paper itself.
+This method was implemented on a laptop computer with a I3 Intel processor that clocks at 2.2 Gigahertz with a RAM size of 4.0 gigabytes.
+Firstly define a Lucas Sequence to be $V_n = V_{n-1}+V{n_2}$ where $V_0 = 2$ and $V_1 = a$ with a being an integer larger than 2.
+Then create a loop that continuously calculates $V_{n!}$ where $n \geq 2$.
+Then after every iteration of this loop calculate the GCD of (N,$V_{n!}-2$) this was done using the Euclid's Algorithm.
+When the GCD is not equal to either 1 or N, then you have a non trivial factor of N.
+The major difficulty of implementing this algorithm was the computational overload of calculating subsequent factorial Lucas Sequences.
+There was a small work around to this to relieve some of the burden of this by recognizing that $V_{n!}(a) = V_n({V_{n-1}})$ meaning if we allow the input to the Lucas sequence to be the output to the previous Lucas Sequence, we can get the factorials of the initial input a without having to actually calculate subsequent factorials of that Lucas Sequence.
+Without this work around even five iterations of this loop quickly became lengthy to calculate, as it would be $V_120$, an extreme amount of stack calls on the limited hardware being used.
+The numbers still become prohibitively large for the hardware fairly quickly, in about 15 iterations.
+So a limit on the number of iterations was engraved in the method (about 15 or so).
+The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had.
+When actually run on the original modulus the algorithm once again found 809 to be a factor about 5 seconds.
+Use of the method on the modulus with 809 divided out produced no further results, even when run for over 20+ hours.
+At this time an estimate for the time the program would actually factor the second modulus has not been produced.
+The only new information that could be extrapolated from this would be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed.
+This ends the discussion of William's P+1 method and our attempt to implement it for our assignment.
+
+\section{The Quadratic Sieve}
+At last we come to the crux of our assignment, The Quadratic Sieve.
+The quadratic sieve is faster for numbers under 100 digits\cite{pomerance}.
+This method was invented by Carl Pomerance in 1981 after a series of enhancements on Fermat's factoring method led to the idea of utilizing smooth numbers to set up a matrix to with enough vectors of which to assure that the squares need for Fermat's method would be found.
+We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
+\\\\
+Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works (similar to the above sections but tackling it in depth).
+Then we will explain our journey through the implementation of the Quadratic Sieve, our problems as well as the solutions to those problems.
+Then we will finally discuss the final results to this assignment.
+\subsection{Basic's of the Algorithm}
+
+\subsection{Application of Linear Algebra}
+\indent For In this section we will talk about the input of Linear Algebra for this algorithm.
+All information in this section not within "A Tale of Two Sieves" will be otherwise sourced.
+Linear Algebra is a key component to the quadratic Sieve Algorithm and is the tool used to actually identify the numbers that would be factors out of all the potential candidates found in the data collection/Sieving phase.
+This component of the Quadratic Sieve method was created when John Brillheart and Michael Morris Utilization multiple linear algebra concepts we convert the smooth numbers found in the earlier stages of the algorithm into exponent vectors.
+As in a vector of the exponents of a numbers prime factors.
+This vector shall be converted into a vector in a finite field of size 2 ($F_2$).
+This is due to the fact that a number is a square if and only if all of it's prime factors exponents add up to zero.
+Thus there is no need to have the vectors number be out of $F_2$.
+The objective of having these vectors is to create a matrix of theses exponent vectors.
+The size of the matrix will be the size of our factor base cross the size of our factor base plus at least 1,(so if $F_B = p_0p_1\dots p_i$ we will have a matrix of size $(ixi)+1$) With this matrix we will use a few properties of linear algebra to find which combination of smooth numbers will give us our factorization.
+\\\\
+\indent So firstly, why do we add the vectors?
+This is because adding the vectors is the equivalent of multiplying the integers themselves in terms of determining if the product of those two numbers (or more) will be a square.
+As an example consider the integers $24 = 2^{3}*3^{1}$ and $15 = 3^{1}*5^{1} $ The exponent vectors for these two will be 110 and 011 the sum vector of these two numbers is not zero and hence the multiple of 24 and 15 is not a square.
+Secondly the reasoning to having one more vector than the size of the factor is due to a linear algebra concept known as Linear dependence.
+Linear dependence tells us that when the number of vectors(rows) exceed the number of dimensions (columns), the sum of a subset of the vectors must be equal to zero.
+Now finding the subset of vectors that equal to zero can be computationally difficult if the matrix became large enough (if you simply try all the combinations ), however there is a technique within Linear Algebra called Gaussian Elimination that can greatly decrease the complexity of finding the zero subset (discussed more in the implementation section).
+Thus by ensuring that the amount of smooth numbers collected exceeds the factor base guarantees that we obtain a square within the resulting matrix.
+Obtaining a factor from the square is not guaranteed however, as half of the possible squares will yield an uninteresting solution.
+So even with the convenience of the matrix there is some luck involved.
+
 \section{Quadratic Sieve}
 
-Quadratic Sieve method is actually discovered step by step.
+Quadratic Sieve method is actually built upon previous factorization method.
 It is a optimization of Dixon's Factorization Method.
-So, to learn what is Quadratic Sieve, we have to understand Dixon's Method.
-And Dixon's Method is also related to Fermat's Factorization and Kraitchik's Factorization Method.
-Here, I will briefly introduce these three factorization methods.
+So, to learn what is Quadratic Sieve, we have to understand Dixon's Method first, which is also related to Fermat's Factorization and Kraitchik's Factorization Method.
+Here, we will briefly introduce these three factorization methods.
 
@@
 \subsubsection {Dixon's Factorization}
-One of the great improvement of Dixon's method comparing to the method before is that he replace the requirement from ``is a square of an integer'' to ``has only small prime factors''.
-To explain this we need introduce 2 concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.
+One of the great improvement of Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''.
+To explain this, we need introduce two concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.
 
@@
 
-\textbf{Smooth Number} is a integer that all its prime factor within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$.
+\textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$.
 We called Q is a \textbf{B-Smooth} Number.
@@
 But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$.
-For each relation is found, it can represent as a exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$.
-And searching the null space of this matrix, could help us to find the square integer.
-Since $M\vec{v} = 0$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to 0, which also implies the products of corresponding Q to that row is a square integer.
-After found the relation, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$
+For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$.
+And searching the null space of this matrix could help us to find the square integer.
+Since $M\vec{v} = \vec{0}$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to $\vec{0}$, which also implies the products of corresponding Q to that row is a square integer.
+After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$
 
 \subsection {Math and Algorithm in Quadratic Sieve}
+Once again, like in previous factoring methods such as in Fermat’s or Dixon’s, we rely on finding two integers, $x$ and $y$,such that N can be expressed as the difference of two squares, $x^{2}-y^{2}$.
+From there we can apply simply algebra find the two factors of $N$, $(x-y)$ and $(x+y)$.
+This may seem simply enough, but how exactly do you find such $x$ and $y$?
+Surely we could try to check every integer $x$, from $sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$.
+For small numbers of $N$, trial division would work fine.
+We, however, don’t need to search the entire interval to find a square.
+Take for example the number $N = 1649$.
+The
+ $\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have\\
+ $41^{2} = 32 = 2^{5}$ \\ $42^{2} = 115 = 5\cdot 23$ \\ $42^{3} = 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.
+ \\\\Note that none of these numbers individually produce a square, but \\$41^{2}\cdot43^{2}\equiv 2^{5}\cdot2^{3}\cdot5^{2}\equiv 2^{8}\cdot5^{2}\equiv (2^{4}\cdot 5)^{2}$ produces a square. 
+ Additionally, even after finding such a and b, we must check if the result is ‘interesting’.
+According to Pomerance, there are “surely plenty of uninteresting pairs $a$,$b$, with $a^{2}-b^{2}(mod  n)$..namely take any value of $a$ and let $b = \pm a$”.
+ However, if we were to instead find an $a$ and $b$ such that $a^{2}\equiv b^{2}(mod N)$, and $b \not\equiv \pm a(mod N)$ then we have found an interesting pair, which would lead to a nontrivial factorization of $N$, through taking the gcd($a\pm b$,$n$).
+This is because although N divides $a^{2}-b^{2}\equiv(a-b)(a+b)$, N does not divide either $(a-b)$ or $(a+b)$ individually because of the second condition.
+Hence non trivial factors $(a-b, N)$ and $(a+b, N)$.
+\\\\
+So instead of searching through the entire interval from $sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well.
+But how exactly do you find such a subsequence?
+Surely we cannot examine all subsequences, for given an interval of length L, there would be $2^{L}$ possible subsequences, in other words, an exponential growth in the number of subsequences as L gets bigger.
+Furthermore, how long of a sequence do we need to examine before we find such a subsequence, and how do we know what the subsequence is?
+\\Well, Pomerance provides us with this lemma:
+\\\\LEMMA.
+If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi{B})$ denotes the number of primes in the interval $[1, B]$, then some non-empty subsequence of ($m_i$) has a product of a square.
+(Pomerance)
+\\\\Recall the definition of B-smooth numbers, where a number is B-smooth if all factors in the prime factorization of said number are less than B.
+Pomerance observes that if a number in the sequence is not B-smooth, than it is unlikely that it will be used in our subsequence.
+This is in observance of the fact that if a number is not B-smooth, the number contains a prime larger than B, and if we were to use this number in our subsequence, there must be one other number which also contains that prime.
+However, if such a prime were large, finding another number with such a prime factor will not be easy, hence why we need some bound B.
+\\Essentially, Pomerance’s lemma states that if we were to find at least $\pi{B}$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square.
+So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi{B}$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$.
+From here we are only interesting in a subsequence of $m_i$’s where there product is a square, but how do we go about finding it?
+Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$.For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1].
+\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2.
+After creating such a $k$ by $j$ matrix, we want to find some number of rows who when combined together form a vector of 0's, the zero vector of length $j$, which is why we need to calculate the null space of the matrix.
+Put simply, the null space of a matrix is the set of all vectors, $v$, such that given a matrix $A$, the product $A\cdot v$, yields the zero vector, which is exactly what we want.
+In our case the null space will yield vectors, each vector containing only entries of 1s and 0s, in which every 1 corresponds to a row in which that $m_i$ belongs to our subsequence.
+\\\\Another problem that arises, however, is selecting such a bound B. What exactly is a good limit for the bound B? 
+\\How do we populate the factor base given a bound B?
+Perhaps it may seem necessary to store a large number of primes in order to sieve, but in fact we can easily generate all primes less than B through applying the Sieve of Eratosthenes:
+\\\\Algorithm: We start with a table of numbers (e.g., 2, 3, 4, 5, .
+.
+.
+) and progressively cross off numbers in the table until the only numbers left are primes.
+Specifically, we begin with the first number, p, in the table, and
+\\1. Declare p to be prime, and cross off all the multiples of that number in the table, starting from $p^{2}$;
+\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1. (O’Niel)
+\\\\Now, the problem is, how do we find the necessary amount of B-smooth numbers needed to factor N?
+Surely, a naive approach would be to trial divide a number by the primes in the factor base until you either get a 1, in which case the number is B-smooth, or you get a number larger larger than B which is not a multiple of any prime in the factor base, in which case it’s not B-smooth.
+Indeed, this approach would be much too slow, given a sufficiently large bound B, B-smooth numbers are far and few between.
+It would be a huge waste of time and resources.
+\\A further improvement could be to only consider numbers which are multiples of primes in the factor base.
+Say in our interval $[\sqrt{N},N]$ and a prime in our factor base, p, we notice that at some point, x, the number $x^{2}-N$ will be a multiple of p, which can be represented as $\sqrt{N}+i$, where i is the distance from the start of the interval.
+From there, every subsequent multiple of p is $k*i$ distance away from $\sqrt{N}$.
+Essentially we will have to solve for $x$ in $x^{2}-N\equiv 0(mod p_i)$, which can yield either 2, 1 or 0 solutions.
+We can do this for every $p_i$ in the factor base and ‘mark’ numbers that are multiples of said prime.
+Then, we will only check marked numbers in our interval by dividing only those primes that marked the number, hence not having to check every number in the interval, and not having to trial divide by every prime in the factor base.
+In the end, this method will work, but does not scale well (as in our case), which is further explained in Sect.
+4.5.
+\\\\
+Additionally, with a defined bound B, should we consider all the primes less than B? Recall the definition of a quadratic residue:
+\\\\
+Definition: An integer q is called a quadratic residue mod n, if it is congruent to a perfect square mod n. In other words, there exists an x such that, $x^{2} \equiv q(mod n)$ 
+\\\\
+When we attempt to sieve, we try to calculate $x^{2}-N\equiv 0(mod p_i)$ where $p_i$ a prime from the factor base, which can be rewritten as $x^{2} \equiv N(mod p_i)$.
+Does this seem familiar?
+Well this essentially boils down to finding out whether or not N is a quadratic residue of $p_i$, in other words, are there solutions, $x$, such that $x^{2}\equiv N(mod p_i)$.
+In effect, not all primes less than $B$ should be in our factor base.
+More specifically, only those primes, $p_i$, less than $B$ such that $N$ is a quadratic residue modulo $p_i$, should be added to our factor base.
+\\Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:
+\\\\
+Definition: The legendre symbol of a and p where p is an odd prime is defined as 
+\\\\
+$\frac{a}{p} = $
+\\$1$ if a is a quadratic residue modulo p and $a\not\equiv 0(mod p)$
+\\$-1$ if a is quadratic non-residue modulo p
+\\$0$ if $a\equiv 0(mod p)$
+\\\\Additionally we will introduce the Law of Quadratic Reciprocity:
+\\\\
+Definition: If p and q are distinct odd primes then:
+\\(a)$(\frac{p}{q})(\frac{q}{p}) = (-1)^{\frac{(p-1)(q-1)}{4}}$
+\\(b)$\frac{1}{p} = 1$
+\\(c)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
+\\(d)$(\frac{2}{p} = (-1)^{\frac{p^{2}-1}{8}})$
+\\\\
+Through applying the Law of Quadratic Reciprocity, it is trivial to calculate $\frac{N}{p_i}$ to find which primes will make N a quadratic residue.
 
@@
 A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which have the leftover in common, the leftover will be canceled.
-In other words, if we can find two partial relations have the same leftover factors we can treat them as two full relations.
+In other words, if we can find two partial relations have the same leftover factors we can treat them as one full relation.
 
@@
 \begin{enumerate}
-\item \textit{Choosing B \& M:} \vspace{2mm}
+\item \textit{Choosing B \& M:} \itemgap
 \\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}.
@@
 
-\item \textit{Building Factor Base:} \vspace{2mm}
+\item \textit{Building Factor Base:} \itemgap
 \\ To build the factor base, first we need to generate primes.
@@
 
-\item \textit{Pre-Sieving:} \vspace{2mm}
+\item \textit{Pre-Sieving:} \itemgap
 \\ In this stage, we did a lot optimizations.
@@
 
-\item \textit{Sieving:} \vspace{2mm}
+\item \textit{Sieving:} \itemgap
 \\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$].
@@
 And then, each client connected to sever and got job from the queue.
-The job could be very large, so we split the job according to the memory of client, and starting multi-thread according to the number of processors of client, and sieving.
+The job could be very large, so we split the job according to the memory of client, and starting multiple threads according to the number of processors of client.
+Then, each thread search different ranges within the job.
 
-\item \textit{Save Sieving Result:}
-\item \textit{Build Exponent Matrix:}
-\item \textit{Finding Null Space:}
-\item \textit{Calculating Factors:}
+\item \textit{Save Sieving Result:} \itemgap
+\\ If we found a relation $\left|sieve\_array[position]-(0.5\log{N}+\log{M})\right| < threshold$ during the sieving, we consider this position is our smooth candidate, and save this position to our candidates set.
+And the reason we use the data structure of set is that it is possible to have duplicate positions and we want avoid checking process.
+We know for a set to check inclusion is very fast, since it just check whether the hash of target is in the table, which is almost $\mathcal{O}(1)$.
+
+When finish sieving, we go through each position we saved, and do trial division.
+We  only record the full relations, and the partial relations with prime leftover.
+And we use millar rabin testing check the primality of the leftover.
+
+And we also record the odd power prime factors, and save these informations to a concurrent set.
+Since this process will do in parallel, we have to keep in mind that concurrency would be a issue, therefore, we need to keep mutual exclusive when we do the save action.
+
+After collecting all the data, the client will sent it back to sever. And sever just simply save them in a file.
+
+\item \textit{Build Exponent Matrix:} \itemgap
+\\ We retrieve the file from sever, and parse it line by line.
+Here we met a problem that still confused us that is even though we collect data in different range , we find duplicates relations.
+This problem force us to collect more relations than we need.
+It could be a bug of our code.
+So, we need check duplication first.
+After that since each line in file correspond to a relation, we need to differentiate full or partial relations.
+if it is full relation we just save $x$ in a list and all the prime factors of $Q(x)$ in a dictionary, prime factor as key, and exponent as value.(why we save this will be explained in \textit{Calculating Factors}).
+Since we have the odd exponent factors information of the relation, it is very simple to use it building a exponent vector and save it in matrix.
+if it is partial relation, we save it a dictionary first, and use the leftover as a key.
+until we find another partial relation have the same leftover, we pop out it from the dictionary, and combine two relation together as following.
+First, we multiply $x_1$ and $x_2$ as $x$, then, merge the two prime factor dictionaries.
+Finally, we xor two exponent vectors and save it in matrix.
+
+Since we did not use the meataxe, we need introduce our matrix implementation.
+The reason why we were not using meataxe is that it is not very well documented, and sometimes it does not work as we expected.
+We are afraid of spending too many time on it.
+And another reason is our number is not insanely large, it just 40000x40000 matrix.
+
+And the reason why it is hard to manipulate large matrix is our ram not big enough to save it.
+Let us do a simple calculation, 40000x40000=1600000000 elements.
+If we use a integer to represent each element that will cost 1600000000*4=6400000000 bytes $\approx$ 6Gb ram.
+This is too memory consuming.
+However, since the matrix is over $\mathcal{F}_2$, we can use binary representation for each element it will only cost 6Gb/32 $\approx$ 190Mb which is acceptable.
+
+Suppose we have a 4x10 matrix below, 
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+matrix data & file representation \\
+\hline
+10010001,01 & 91,40 \\
+\hline
+11010001,01 & d1,40 \\
+\hline
+00110001,01 & 31,40 \\
+\hline
+00010100,10 & 14,80 \\
+\hline
+\end{tabular}
+\end{table}
+
+First, we make a very simple header, which only has two integers that specific the row number and the column number.
+Then, we use 1 byte to represent 8 bits, and if the matrix's column size mod 8 is not 0, we are padding zeros after each row.
+For example 01 becomes 01000000 which is 40 in hex.
+This is for sake of simplicity of implementation.
+And finally, we just save each row linearly.
+
+To access certain rows, say the 8th row, we have our initial position pointer $s$, and we calculate many bytes in each row by row\_length = (column+padding)/8, and the start position of 8th row is 8*row\_length+$s$.
+
+To access certain column, say the 6th column, we calculate this column in which byte by 6/8=0, this means 6th column belongs to the first byte, then, take the byte and right shift 6 position and do a ``and'' operation with 1 which means ignore other bits except for the last bit.
+
+\item \textit{Finding Null Space:} \itemgap
+
+We use Gaussian elimination to find the null space.
+The reason why we can use Gaussian elimination to find null space, is because any elementary row operation can be seen as a matrix transformation.
+For example.
+
+An elementary row operation $M\xrightarrow{R1\rightarrow R1+2\times R2}M^\prime$
+$$
+\begin{bmatrix}
+ 1 & 2 & 3 \\
+ 1 & 1 & 2 \\
+ 2 & 2 & 4
+\end{bmatrix}\xrightarrow{R1\rightarrow R1+2\times R2}
+\begin{bmatrix}
+ 3 & 4 & 7 \\
+ 1 & 1 & 2 \\
+ 2 & 2 & 4
+\end{bmatrix}
+$$
+
+can be represented as $EM=M^\prime$
+
+$$
+\begin{bmatrix}
+ 1 & 2 & 0 \\
+ 0 & 1 & 0 \\
+ 0 & 0 & 1
+\end{bmatrix}
+\begin{bmatrix}
+ 1 & 2 & 3 \\
+ 1 & 1 & 2 \\
+ 2 & 2 & 4
+\end{bmatrix} \rightarrow
+\begin{bmatrix}
+ 3 & 4 & 7 \\
+ 1 & 1 & 2 \\
+ 2 & 2 & 4
+\end{bmatrix}
+$$
+
+So, if we reduce $M$ to its reduced echelon form $M^\prime$ by Gaussian Elimination, means that $\exists E=\prod_{i=1}^k{E_i}\ s.t.\ EM \rightarrow M^\prime$, where $E_i$ is the elementary row operation.
+We also know at the bottom of reduced echelon form always have all zero rows, and that is the null space.
+
+Our approach is to records all the elementary operation by using a identity matrix $I$ since $EI=E$.
+
+\item \textit{Calculating Factors:} \itemgap
+
+First, we will going to explain why finding null space is equal to find the sum of rows equal to zero.
+It is easy only if you notice that and none of the resources we read explained this.
+It is just because the matrix production is for each row multiply a coefficient add rows together.
+And we are working over $\mathbb{F}_2$, the multiplier 0 means not using this row, 1 means using this row.
+And this is the reason why we are checking each element of the vector in null space, if we found a 1, we find the corresponding row in matrix and get related $x$ and all the prime factors of $Q(x)$.
+
+Recall that in \textit{Building Exponent Matrix} Section, we said we will explain why we save all the prime factors of $Q(x)$ instead of just saving $Q(x)$ itself.
+The reason is that if we multiply these $Q(x)$ , we get an insanely large number, we do not know any good algorithm to find the square root of it, we tried newton's square root approximation, which did not help us much.
+We can not get a accurate number.
+Therefore, we saved all the prime factor and their exponents.
+And then, we only need to half of the exponent and multiply them together we get the $\sqrt{\prod Q(x)}$.
+
+After we got $\sqrt{\prod Q(x)}$, our final answer is $gcd\left(\prod Q(x) \pm \prod x, N\right)$, if we are lucky not all relation we've found are trivial, we have one factor of N.
 
 \end{enumerate}
-
-\subsection {Results of Experiments}
 
@@
 
+\bibitem{silverman} Robert D. Silverman, [\textit{The Multiple Polynomial Quadratic Sieve}], Mathematics of Computation, Volume 48, Issue 177(Jan., 1987), 329-339.
+
+\bibitem{bosko} LINDSEY R. BOSKO, [\textit{FACTORING LARGE NUMBERS, A GREAT WAY TO SPEND A BIRTHDAY}]
+
+\bibitem{twenty} Dan Boneh, [\textit{Twenty Years of Attacks on the RSA Cryptosystem}]
+
+\bibitem{atale} Carl Pomerance, [\textit{A Tale of Two Sieves}], December 1996
+
+\bibitem{joy} Samuel S. Wagstaff, Jr., [\textit{The Joy Of Factoring}], STUDENT MATHEMATICAL LIBRARY Volume 68, 2013, Chapter 8
+
+\bibitem{simple} Eric Landquist, [\textit{The Quadratic Sieve Factoring Algorithm}], December 14, 2001, Graduation Paper
+
+\bibitem{pomerance} Pomerance, [\textit{Smooth Numbers and the Quadratic Sieve }], Algorithmic Number theory MIRI Publication Volume 44, 2008
+\bibitem{williams} H.C. Williams, [\textit{A p+1 Method of Factoring}], Mathematics of computation volume 39, Number, 159 July 1982
+
 \end{thebibliography}

### 2016-11-29 RSACracking/src/cracking/SmoothNumberFileParser.java

@@ -16,9 +16,11 @@ import static cracking.algorithms.MathOp.modInverse;
 import cracking.algorithms.Primes;
 import cracking.cluster.SmoothInfo;
 import static cracking.utils.Util.error;
+import java.io.BufferedReader;
+import java.io.FileInputStream;
 import java.io.FileNotFoundException;
 import java.io.IOException;
-import java.io.RandomAccessFile;
+import java.io.InputStreamReader;
 import java.math.BigInteger;
 import static java.math.BigInteger.ONE;
 import static java.math.BigInteger.ZERO;
@@ -47,7 +49,7 @@ public class SmoothNumberFileParser {
     
     private static final BiFunction<BigInteger, BigInteger, BigInteger> Qx = (x, N)->x.pow(2).subtract(N);
 
-    private RandomAccessFile file;
+    private BufferedReader file;
     private int[] fb;
     private BigInteger N;
     private HashSet<BigInteger> relationDupChecker;
@@ -63,7 +65,7 @@ public class SmoothNumberFileParser {
     }
     
     public SmoothNumberFileParser(String filePath, int B, BigInteger N) throws FileNotFoundException, IOException {
-        file = new RandomAccessFile(filePath, "r");
+        file = new BufferedReader(new InputStreamReader(new FileInputStream(filePath)));
         relations = new ArrayList<>();
         factors = new ArrayList<>();
         relationDupChecker = new HashSet();
@@ -105,14 +107,13 @@ public class SmoothNumberFileParser {
     }
     
     private void parse() throws IOException {
-        long len;
         try {
-            len = file.length();
+            String line = null;
             int i = 0;
             int rows = expMatrix.getRows();
-            while(file.getFilePointer() < len) {
+            while((line = file.readLine()) != null) {
                 if(i >= rows) break;
-                SmoothInfo info = SmoothInfo.fromString(file.readLine());
+                SmoothInfo info = SmoothInfo.fromString(line);
                 if(info.getLeftover() == null) {
                     if(relationDupChecker.contains(info.getX())) {
                         continue;
@@ -211,7 +212,11 @@ public class SmoothNumberFileParser {
         return power;
     }
     
-    public List<BigInteger> calculateFactor(BigInteger N, int[][] nullSpace) {
+    public List<BigInteger> calculateFactor() throws IOException {
+        return calculateFactor(expMatrix.nullSpace());
+    }
+    
+    public List<BigInteger> calculateFactor(int[][] nullSpace) {
[…]

### 2016-11-29 RSACracking/src/cracking/algorithms/LargeGF2Matrix.java

@@ -237,7 +237,7 @@ public class LargeGF2Matrix implements AutoCloseable {
         boolean[] marker = new boolean[R];
         int onePercent = C/100;
         for(int c=0; c<C; c++) {
-            if(onePercent!=0 && c % onePercent == 0) System.out.printf("calculate matrix: %d percent \n", c/onePercent);
+//            if(onePercent!=0 && c % onePercent == 0) System.out.printf("calculate matrix: %d percent \n", c/onePercent);
             LinkedList<Integer> rows = getLeftMostOneRows(c, marker);
             if(rows.isEmpty()) continue;
             int pivot = rows.poll();
@@ -266,19 +266,19 @@ public class LargeGF2Matrix implements AutoCloseable {
     }
     
     public static void main(String[] args) throws IOException {
-//        try (LargeGF2Matrix matrix = new LargeGF2Matrix(10, 10, "./testM")) {
-//            matrix.rowAdd(0, new int[]{1,0,0,1,0,0,0,1,0,1});
-//            matrix.rowAdd(1, new int[]{1,0,0,1,0,0,0,1,0,1});
-//            matrix.rowAdd(2, new int[]{1,1,0,1,0,0,0,1,0,1});
-//            matrix.rowAdd(3, new int[]{0,0,1,1,0,0,0,1,0,1});
-//            matrix.rowAdd(4, new int[]{1,0,0,1,0,0,0,1,1,1});
-//            matrix.rowAdd(5, new int[]{1,0,0,0,0,0,0,1,1,0});
-//            matrix.rowAdd(6, new int[]{0,0,0,1,0,1,0,0,1,0});
-//            matrix.rowAdd(7, new int[]{0,0,0,1,0,0,1,0,0,1});
-//            matrix.rowAdd(8, new int[]{0,0,1,0,0,1,0,0,0,0});
-//            matrix.rowAdd(9, new int[]{0,0,0,1,0,0,0,1,0,0});
-//            matrix.toMeatAxeBinaryFile("./testMeataxe");
-//        }
+        try (LargeGF2Matrix matrix = new LargeGF2Matrix(10, 10, "./testM")) {
+            matrix.rowAdd(0, new int[]{1,0,0,1,0,0,0,1,0,1});
+            matrix.rowAdd(1, new int[]{1,0,0,1,0,0,0,1,0,1});
[…]

### 2016-11-29 RSACracking/src/cracking/algorithms/QuadraticSieve.java

@@ -22,6 +22,7 @@ import static cracking.algorithms.Primes.RandomPrimeGenerator.ODD_FUNC;
 import static cracking.algorithms.Primes.findClosePrime;
 import static cracking.algorithms.Primes.millerRabinTest;
 import cracking.cluster.SmoothInfo;
+import cracking.utils.Util;
 import static cracking.utils.Util.error;
 import static cracking.utils.Util.mustPositive;
 import java.io.File;
@@ -37,9 +38,11 @@ import static java.math.BigInteger.ZERO;
 import static java.math.BigInteger.valueOf;
 import java.util.Arrays;
 import static java.util.Arrays.stream;
+import java.util.HashMap;
 import java.util.HashSet;
 import java.util.Iterator;
 import java.util.Set;
+import java.util.Vector;
 import static java.util.stream.Collectors.toSet;
 import java.util.stream.IntStream;
 
@@ -268,31 +271,39 @@ public class QuadraticSieve implements Runnable {
     public static void main(String[] args) throws FileNotFoundException, IOException {
         
 //        BigInteger N1 = Main.TARGET; //new BigInteger("6275815110957813119593022531213");
-        BigInteger N1 = new BigInteger("489293762578746481445307920902864380533");
-//        BigInteger N1 = new BigInteger("6275815110957813119593022531213"); //new BigInteger("13290059");
-        int B = 150_000;
-        QuadraticSieve sieve = new QuadraticSieve(N1, B, 80_000_000);
+//        BigInteger N1 = new BigInteger("489293762578746481445307920902864380533");
+        
+        Primes.RandomPrimeGenerator randomGen = new Primes.RandomPrimeGenerator();
+        BigInteger b1 = randomGen.gen(6).next();
+        BigInteger b2 = randomGen.gen(7).next();
+        BigInteger N1 = b1.multiply(b2);
+        System.out.println(N1);
+        int B = 100;
+        int M = 500;
+        QuadraticSieve sieve = new QuadraticSieve(N1, B, M);
 //        System.out.println(Arrays.toString(Factorization.fastFactorBase(B, N1)));
         Set<SmoothInfo> relations = new HashSet<>();
         sieve.setBSmoothRef(relations);
         sieve.run();
+        
         File file = new File("./testRelation");
         if(file.exists()) file.delete();
         file.createNewFile();
         PrintStream ps = new PrintStream(file);
         relations.forEach(ps::println);
[…]

### 2016-11-29 Paper/Paper.tex
Yiwei Merging

@@
 
+In this paper, we will assume Alice is the message sender and Bob is the message receiver who receives messages from Alice.
+Eve is the malicious devil attacker to try to intercept and decrypt the message.
+And d represents the private key.
+
+\section{Attacks on Misused RSA}
+	Since factoring the large number, N, is a hard problem, our objective in this section is to decrypt the encrypted message without directly factoring N.
+	Unfortunately, most of these special attacks are based on misuse of RSA.
+	So, if the numbers, structures and implementation of RSA are designed well and used properly, these kinds of attacks are not applicable against RSA.
+
 \subsection{ Common Modulus Attack}
 		Assume the same common modulus N is used by all the users under a system, so each user i gets a unique public key pair $<N,e_i>$ and a unique private key pair $<N,d_i>$ from the central system.
-		Now, Alice is sending an encrypted message C = $M^{e_{Alice}}$ mod N to Bob (Bob has to know either factors of N or to do the same thing with Eva). 
+		Now, Alice is sending an encrypted message C $\equiv$ $M^{e_{Alice}}$ mod N to Bob. 
 		However, another user Eve can also get Alice's original message by using her own keys, ${e_{Eve}}$ and ${d_{Eve}}$, to factor common modulus N. There are many ways to factor N if we know e and d.
-		For example, we can guess $\phi(n)$  from ed = 1 (mod $\phi(n)$).
-Since ed -1 = k$\phi(n)$ = k$2^x$r (because $\phi(n)$ must be an even number, $\phi(n)$ can be expressed in powers of 2 times an odd number with a certain integer k),
-		we can get correct $\phi(n)$ in $\log_2(N)$.
-		Or if we are lucky enough that N = pq, $\phi(n)$ = (p-1)(q-1) = pq - (p+q) +1 = n - (p+q) +1.
-Then q = (n- $\phi(n)$ +1)-p.
-By Substituting q into N =pq, N = p(n- $\phi(n)$ +1)-p), which is equal to $p^2$ - p(n-$/phi(n)$+1)+n =0.
-		Now we can factor N by solving this quadratic equation.
+		For example, we can guess $\phi(N)$  from ed $\equiv$ 1 (mod $\phi(N)$).
+Since ed -1 = k$\phi(N)$ = k$2^x$r (because $\phi(N)$ must be an even number, $\phi(N)$ can be expressed in powers of 2 times an odd number with a certain integer k),
+		we can guess correct $\phi(N)$ in $\log_2(ed-1)$.
+		And if we are lucky enough that N = pq with p and q are primes, $\phi(N)$ = (p-1)(q-1) = pq - (p+q) +1 = N - (p+q) +1.
+Then q = (N- $\phi(N)$ +1)-p.
+By Substituting q into N =pq, N = p(N- $\phi(N)$ +1)-p), which is equal to $p^2$ - p(N-$\phi(N)$+1)+N =0.
+		Now we can factor N by solving this quadratic equation with guessed $\phi(N)$.
 
-		After Eve knows the factors of N, she can compute $\phi(N)$ and compute ${d_{Alice}}$ ${e_{Alice}}$ = 1 mod $\phi(N)$ to find ${d_{Alice}}$ by Euclidean algorithm (since ${e_{Alice}}$ is public information).
+		After Eve knows the factors of N, she can compute $\phi(N)$ and compute ${d_{Alice}}$ ${e_{Alice}}$ $\equiv$ 1 mod $\phi(N)$ to find ${d_{Alice}}$ by Euclidean algorithm (since ${e_{Alice}}$ is public information).
 		Then Eve can recover Alice's M = $C^{d_{Alice}}$ mod N.
@@
 		However, we are only given one public key $<N,e>$ and there are no other users involving in our case. So, this attack does not apply to our case.
-\subsection{Blinding Attack on RSA signature}
-		Assume Alice has a public key pair $<N,e>$ and a private key pair $<N,d>$.
-Eve asks for Alice to sign a random message M' (M' = $r^eM$ with r picked by Eve randomly and M is the targeted high secret message).
-		Then, by the fact that signature S' = $M'^d$ mod N and S = s'/r, Eve can recover M by computing $S'^e/r^e$ since $S^e$ = $(S')^e/r^e$ = $(M')^ed / r^e$ = $M'/r^e$ = M mod N.
 
-		Our problem doesn't involve in digital signature.
 \subsection{Small private Exponent Attack}
+        The decryption time of the RSA mechanism is tied directly to the time it takes to do the exponentiation of $ M^{ed} $.
+The time it takes is linear in $log_{2}d $.
+So utilizing a small private exponent can greatly improve the speed of the RSA mechanism.
+However, there exists an attack that
+works for any pair (e,d) where $d$ is below $ \frac{1}{3}N^{\frac{1}{4}} $ based on a theorem by M.Weiner [4].
+This theorem utilizes continued fractions to show that d can be approximated in linear time when it is small enough for the computations to remain feasible.
 
-		1. d has to be large enough to be secure (drawback: large d would take more computation time and a large storage space for smart cards)
-
-		2. d can be recovered in linear time if d is small
-		it does not apply to our case because we don't have information about d so that it would be inefficient to apply this attack.
+The issue with this attack in relation to our question remains the lack of any information regarding d, so it would be inefficient to apply this attack.
 
 \subsection{ Small public Exponent Attack}
-		Sometimes it is possible that we use small small public exponent in order to reduce encryption time.
-However, it is not secure and we show several methods to break RSA by having small public exponent as following.
+		Sometimes it is possible that we use small public exponent in order to reduce encryption time.
+However, it is not secure and we will show several methods to break RSA by having small public exponent as following.
 
 \subsubsection{Hastad's Broadcast Attack}
-		Assume Alice wants to send a message to many users (k of them). It is possible that Alice is lazy to compute $M^(e_i)$ according to each user, so she may choose the same e for all users.
+		Assume Alice wants to send a message to many users (k of them). It is possible that Alice is lazy to compute $M^{e_i}$ according to each user, so she may choose the same e for all users.
 		Then She first encrypts the message M according to a user's public key pair $<N_i, e>$ by $M^e$ (mod $N_i$) = $C_i$ and sends the cipher text $C_i$ to the corresponding user i. 
@@
 Then she applies the Chinese Remainder Theorem to each $C_i$, which gives C' = $M^k$ (mod ($N_1$)*($N_2$)*...*($N_k$)).
-		Since M is less than all $N_i$, $M^k$ < ($N_1$)*($N_2$)*...*($N_k$) is satisfied, which means C' = $M^k$. So, Eve can recover M by taking k root of C'.
+		Since M is less than all $N_i$, $M^k$ $<$ ($N_1$)*($N_2$)*...*($N_k$) is satisfied, it means C' = $M^k$. So, Eve can recover M by taking k root of C'.
 		This attack is efficient only when e is the same for all users and e is small.
@@
 \subsubsection{Franklin-Reiter Related Message Attack}
+		The Franklin-Reiter related message attack is an attack that involves a situation where recipients send a series of messages where $M_1 = f(M_2)$ with $M_1M_2 \in \mathbb{Z}^{*}_N[x] $.
+These Messages are encrypted with the same modulus.
+Now given the $C_1$ and $C_2$ along with the public key (N,e) $M_1$ and $M_2$ can be recovered in quadratic time in log(N).
+A specific proof is given in the "20 years of \dots RSA" [4].
+This attack is only computationally feasible with small public exponents.
 
-		it does not apply to our case because it has to send related messages using same modulus N. In our case, we only intercept one message.
+		This attack once again cannot be used for our problem for the reason of only being given one M, though perhaps it could be possible to construct an M such that $ M_2 = f(M_1) $.
+It however was not the line of attack we ultimately went with.
+
+\subsubsection{Partial Key Exposure}
+A partial key exposure attack involves a situation where if an attacker can expose around a quarter of the bits of the private key, he can construct the rest of d providing the public exponent is small (small meaning $e <\sqrt[]{N}$ where N and e are the public RSA key).
+This attack was developed when the above statement was discovered by Boneh,Durfee and Frankel.
+There is involved in this attack which I will outline below (quoted from "20 years \dots RSA" [4].)
+\\\\
+\textbf{Theorem (BDF): }\textit{Let (N,d) be an RSA private key in which N is n bits long.
+Given the $\left\lceil n/4 \right\rceil$ least significant bits of d.
+Marvin can reconstruct d in time linear in $elog_2e$}
+\\\\
+The proof of this relies on a second theorem from Coppersmith which we will not be outlining at this time.
+This attack is actually interesting do to a statement that it may be possible to get the RSA system to leak a portion of the significant bits of the private key and with a few equations be able to approximate the private key.
+We ultimately did not pursue this line of attack due to fears of spending too much time on a potentially fruitless line of attack.
 
 \subsection{implementation attacks}
-	it does not apply to our case because it needs to measure the time it takes for decryption. In our case, we do not have such information.
-
+The implementation attacks involve attacks against applications of RSA rather than the RSA mechanism itself. These
+attacks involve timing attacks, attacks involving computer glitches and one involving the an RSA message padded using
+the public key cryptography standard 1. These attacks are incompatible with our problem to a much higher degree than
+the other attacks so we won't go into to details about them.
 \section{Factoring Attacks Against RSA}
@@
 
+\section {Decoding the message}
+
+Once we got the factors of N, we use Euler-totient function calculates the $\varphi(N)$, and then we can calculate the private key $d$ by find the mod inverse of $e \mod{\varphi(N)}$ thorough extend euclidean gcd algorithm.
+After we got $d$ we can recover the message just by taking $(m^e)^d \pmod{n}$.
+
+Then, we got a message encoded as 1121225152171520201541591920182520182511292020125\\2051445181451919.
+Since, we know it is English and the encoding method already, we use three methods to recover it to English very quickly.
+\renewcommand\labelenumi{\arabic{enumi}.}
+\begin{enumerate}
+\item We use a English dictionary, and encodes the words exactly the same way as the message did.
+And we only searching for the longer words(at least 4 letters).
+And we extract the matching part, which could shrink the length of the message.
+In our case, we use this method found the word ``tenderness''.
+
+\item We wrote a program to calculate all the possible combinations. The idea is using backtrack algorithm to build a tree. Then, saving all the leaves in the tree. 
+\end{enumerate}
+
 \pagebreak

### 2016-11-29 Paper/Paper.tex
update Decode Message

@@
 		In this month, we search up to 58248674129 (35-bit), which is 21 digits difference with the second prime factor 64820903298591432157114065708311(105-bit).
-		And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search.
-		Moreover, the completely search from 1 to N will take about 5*$10^{55}$ years. (all the calculations above are done by Java) 
+		And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search. (all the calculations above are done by Java) 
 		Therefore, if we only use brute force search to factor N, we won't be able to reach the solution until 7.6*$10^{16}$ generations after (and each generation should continue this task non-stop).
@@
  \subsubsection{Pollard's Rho method}
-		Assume we want to factor a positive number N. We begin by randomly selecting with replacement from the set $S_1$ = {0,1,2,...,N-1} to form a sequence $x_1$, $x_2$, $x_3$,.... 
-		Define $x_i$' = $x_i$ mod p so that our sequence is now $x_1$', $x_2$',$x_3$',... with each $x_i$' belongs to $S_2$ = {0,1,2,...,p-1}.
+		Assume we want to factor a positive number N. We begin by randomly selecting with replacement from the set $S_1$ = \{0,1,2,...,N-1\} to form a sequence $x_1$, $x_2$, $x_3$,.... 
+		Define $x_i$' = $x_i$ mod p so that our sequence is now $x_1$', $x_2$',$x_3$',... with each $x_i$' belongs to $S_2$ = $\{0,1,2,...,p-1\}$.
 		Because the sets $S_1$,$S_2$ are finite, eventually there will be a repeated integer in both sequence.
@@
 Since, we know it is English and the encoding method already, we use three methods to recover it to English very quickly.
+
 \renewcommand\labelenumi{\arabic{enumi}.}
@@
 
-\item We wrote a program to calculate all the possible combinations. The idea is using backtrack algorithm to build a tree. Then, saving all the leaves in the tree. 
+\item We wrote a program to calculate all the possible combinations.
+The idea is using backtrack algorithm to build a tree.
+Then, saving all the leaves in the tree.
+Finally, collecting each path from the leaf to root.
+The example for code 21525 in below:
+
+\pagebreak
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\textwidth]{tree.png}
+\end{figure}
+
+and we use this little program to list all possibilities to give us hints.
+
+\item Since the message is not very long and encoding method is easy, we just use our English knowledge to test whether the words make sense in its place.
+
 \end{enumerate}
 
+And finally, we solve this assignment.
+
 \pagebreak
+
 \begin{thebibliography}{99}

### 2016-11-29 Paper/Paper.tex
Merge ours

@@
 The data we were given is simply the public key, and the cipher modulus.
-The problem has specified that the message was encrypted to number format by each being equal to a set of one or two number (Ex: A = 1,B = 2,with Z = 26).
+The problem has specified that the message was initially encoded to a number, where each letter corresponds to an integer from 1 to 26 (Ex: A = 1,B = 2,...
+Z = 26).
 
@@
 
-\indent This is all the information afforded to us to solve the problem of recovering the message.
-Now we will discuss potential attacks against RSA and the pitfalls of many of them given the information provided.
-
-In this paper, we will assume Alice is the message sender and Bob is the message receiver who receives messages from Alice.
-Eve is the malicious devil attacker to try to intercept and decrypt the message.
-And d represents the private key.
+	\indent This is all the information afforded to us to solve the problem of recovering the original message.
+Now we will discuss potential attacks against RSA, their pros/cons, and whether or not we can actually use such attacks with the given information provided.
 
@@
 	\\\\
-The proof of this relies on a second theorem from Coppersmith which we will not be outlining at this time.
-This attack is actually interesting do to a statement that it may be possible to get the RSA system to leak a portion of the significant bits of the private key and with a few equations be able to approximate the private key.
+	The proof of this relies on a second theorem from Coppersmith which we will not be outlining in this paper.
+This attack is actually interesting to implement due to the statement that it may be possible to get the RSA system to leak a portion of the significant bits of the private key and with a few equations be able to approximate the private key.
 We ultimately did not pursue this line of attack due to fears of spending too much time on a potentially fruitless line of attack.
 
-\subsection{implementation attacks}
+	\subsection{Implementation Attacks}
 	The implementation attacks involve attacks against applications of RSA rather than the RSA mechanism itself. These
@@
 	\section{Factoring Attacks Against RSA}
-\subsection{Special Factoring Methods}
+	\subsection{Special-Purpose Factoring Methods}
 	The efficiency of this type of methods usually depends on the size of the first prime factor or some special form of N.
-If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fast.
-		Thus, we usually apply these special factoring methods to find whether there is a small prime factor to divide N so that we can decrease the size of N before proceed with the general factoring methods.
+If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fairly quickly.
+	Thus, we usually apply these special factoring methods to quickly discover whether there is a small prime factor or not, which we can then divide N by, so that we can decrease the size of N(though not by much) before proceeding with the general factoring methods.
 
 	\subsubsection{ Brute Force}
-		The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increase by 2.
-		In this month, we search up to 58248674129 (35-bit), which is 21 digits difference with the second prime factor 64820903298591432157114065708311(105-bit).
+	The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increasing by 2.
+	In this month, we searched up to 58248674129 (35-bit), which is a 21 digits difference from the second prime factor 64820903298591432157114065708311(105-bit) which we found later on using Quadratic Sieving.
 	And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search. (all the calculations above are done by Java) 
@@
 Say $p$ and $q$ are prime factors of the number we want to factor, $N$.
-If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L-1}$.
-From there we can calculate gcd($a^{L-1}$, $N$), which we can have two cases.
-The first case is if the gcd($a^{L-1}$, $N$) is not equal to $N$, which means that the gcd must be our prime factor p (since $a^{L-1} = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$).
-The second case is if gcd($a^{L-1}$, $N$) = $N$, which implies that $N| a^{L-1}$.
-In this case $q$ will also divide $a^{L-1}$, meaning $a^{L} = 1(mod q)$ (because $a^{L-1} = 0(mod q)$).
+If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L}-1$.
+From there we can calculate gcd($a^{L}-1$, $N$), which we can have two cases.
+The first case is if the gcd($a^{L}-1$, $N$) is not equal to $N$ or $1$, which means that the gcd must be our prime factor p (since $a^{L}-1 = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$).
+The second case is if gcd($a^{L}-1$, $N$) = $N$, which is uninteresting, in which case we should try a different a.
+	\\In other words, since we do obviously do not know p, we cannot calculate $a^{p-1}-1$ explicitly so we try instead a multiple of (p-1), say m = k(p-1).
+The idea is that we do not need to exponentiate exactly up to $p-1$, but a smaller exponent, $k(p-1)$ instead.
+We need to choose an integer for m such that we get a factor of $n$ if $p-1|m$.
+By choosing m to be a product of many small primes, the chances that this condition holds will increase.\cite{charest}
 	\\\\Algorithm 
@@
 	\\\\
-Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$, and take the product of all primes < $B$ as well, with an increasing $B$ instead of $r!$.
-The goal is to find an $L$ such that it is a large multiple of $p-1$
+	Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$ as in other implementations \cite{charest} and take the product of primes, $p_i^{\frac{log B}{logp_i}}$ less than $B$ as well, with an increasing $B$ instead of an increasing $r!$.
+Again, the goal is to ultimately find some exponent, $L$, such that $p|a^{L}-1$ in which the gcd($a^{L}-1$,$N$) = d where $1\le d\le N$.
 	\\\\An attempt at factoring our $N$ using Pollard’s $p-1$ factoring algorithm also proved to yield similar results with Pollard rho factorization.
@@
 	\section{The Quadratic Sieve}
-At last we come to the crux of our assignment, The Quadratic Sieve.
-The quadratic sieve is faster for numbers under 100 digits\cite{pomerance}.
-This method was invented by Carl Pomerance in 1981 after a series of enhancements on Fermat's factoring method led to the idea of utilizing smooth numbers to set up a matrix to with enough vectors of which to assure that the squares need for Fermat's method would be found.
+	At last, we had reached the conclusion that we may have to implement the Quadratic Sieve in order to factor our N.
+According to Carl Pomerance, the mind behind the Quadratic Sieve, the Quadratic Sieve is the fastest for numbers under 100 digits\cite{pomerance}.
+This method was created after a series of enhancements on Fermat's factoring method utilizing smooth numbers, and matrices of exponent vectors in order to assure that such a square needed for Fermat's method would be found.
 We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
 	\\\\
-Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works (similar to the above sections but tackling it in depth).
-Then we will explain our journey through the implementation of the Quadratic Sieve, our problems as well as the solutions to those problems.
-Then we will finally discuss the final results to this assignment.
+	Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works.
+We will then explain our our task of implementing the Quadratic Sieve, as well as the problems that we were faced with.
 	\subsection{Basic's of the Algorithm}
@@
 	\subsubsection {Kraitchik's Factorization}
-Kraitchik's method is instead of checking $x^2-n$ is a square, he suggests to check $x^2 - kn$ a square number, which is equivalent to find $y^2 \equiv x^2 \pmod{n} $.
+	Kraitchik's method is to instead of checking whether or not $x^2-n$ is a square, we check whether or not $x^2 - kn$ is a square number, which is equivalent to find $y^2 \equiv x^2 \pmod{n} $.
 And the only interesting solution is $ x \not\equiv \pm y \pmod{n}$.
 Besides this, instead of seeking one $x^2-n$ is square, he was looking for a set of number $ \{x_1, x_2, \dots, x_k\} $ such that $\displaystyle y^2 \equiv \prod_{i=1}^k{(x_i^2 - n)} \equiv \prod_{i=1}^k{x_i^2} \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n} $ is square.
-if he can find a relation like this, then, the factors of n is $\displaystyle gcd(|y \pm \prod_{i=1}^k{x_i}|, n)$
+If he can find a relation like this, then, the factors of n is just $\displaystyle gcd(|y \pm \prod_{i=1}^k{x_i}|, n)$
 
 	\subsubsection {Dixon's Factorization}
-One of the great improvement of Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''.
-To explain this, we need introduce two concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.
+	One of the greater improvements found in Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''.
+To explain this, we need introduce two concepts which are \textbf{Factor Bases} and \textbf{Smooth Numbers}.
 
-\textbf{Factor Base} is a set of prime factors $S_{fb}=\{p | p \le B\}$ where $B$ is some integer.
+	A \textbf{Factor Base} is a set of prime factors $S_{fb}=\{p | p \le B\}$ where $B$ is some integer.
 
-\textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$.
-We called Q is a \textbf{B-Smooth} Number.
+	A \textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$.
+We call Q a \textbf{B-Smooth} Number.
 
@@
 But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$.
-For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$.
-And searching the null space of this matrix could help us to find the square integer.
+For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$.
+After finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$ and searching the null space of this matrix could help us to find the square integer.
 Since $M\vec{v} = \vec{0}$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to $\vec{0}$, which also implies the products of corresponding Q to that row is a square integer.
-After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$
+After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is simply $gcd(y\pm x, n)$
 
-\subsection {Math and Algorithm in Quadratic Sieve}
+	\subsection {Algorithm in Quadratic Sieve}
 	Once again, like in previous factoring methods such as in Fermat’s or Dixon’s, we rely on finding two integers, $x$ and $y$,such that N can be expressed as the difference of two squares, $x^{2}-y^{2}$.
-From there we can apply simply algebra find the two factors of $N$, $(x-y)$ and $(x+y)$.
+From there we can apply simply algebra to find the two factors of $N$, $(x-y)$ and $(x+y)$.
 This may seem simply enough, but how exactly do you find such $x$ and $y$?
-Surely we could try to check every integer $x$, from $sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$.
-For small numbers of $N$, trial division would work fine.
+Surely we could try to check every integer $x$, from $\sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$, not to mention how you would actually check if $x^{2}-N$ is a perfect square.
 We, however, don’t need to search the entire interval to find a square.
@@
 The
- $\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have\\
- $41^{2} = 32 = 2^{5}$ \\ $42^{2} = 115 = 5\cdot 23$ \\ $42^{3} = 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.
+	$\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have
+	\\\\
+	$41^{2} - N = 32 = 2^{5}$ \\ $42^{2} - N= 115 = 5\cdot 23$ \\ $42^{3} - N= 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.
 	\\\\Note that none of these numbers individually produce a square, but \\$41^{2}\cdot43^{2}\equiv 2^{5}\cdot2^{3}\cdot5^{2}\equiv 2^{8}\cdot5^{2}\equiv (2^{4}\cdot 5)^{2}$ produces a square. 
@@
 	\\\\
-So instead of searching through the entire interval from $sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well.
+	So instead of searching through the entire interval from $\sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well.
 But how exactly do you find such a subsequence?
@@
 	\\\\LEMMA.
-If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi{B})$ denotes the number of primes in the interval $[1, B]$, then some non-empty subsequence of ($m_i$) has a product of a square.
+If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi\left(B\right)$ denotes the number of primes in the interval $[1, B]$), then some non-empty subsequence of ($m_i$) has a product of a square.
 (Pomerance)
@@
 However, if such a prime were large, finding another number with such a prime factor will not be easy, hence why we need some bound B.
-\\Essentially, Pomerance’s lemma states that if we were to find at least $\pi{B}$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square.
-So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi{B}$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$.
+	\\\indent Essentially, Pomerance’s lemma states that if we were to find at least $\pi\left(B\right)$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square.
+So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi\left(B\right)$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$.
 From here we are only interesting in a subsequence of $m_i$’s where there product is a square, but how do we go about finding it?
-Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$.For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1].
-\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2.
+Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$.
+For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1].
+	\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested in whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2.
 After creating such a $k$ by $j$ matrix, we want to find some number of rows who when combined together form a vector of 0's, the zero vector of length $j$, which is why we need to calculate the null space of the matrix.
@@
 In our case the null space will yield vectors, each vector containing only entries of 1s and 0s, in which every 1 corresponds to a row in which that $m_i$ belongs to our subsequence.
-\\\\Another problem that arises, however, is selecting such a bound B. What exactly is a good limit for the bound B? 
-\\How do we populate the factor base given a bound B?
+	\\\\You may also ask, how we would populate the factor base given a bound B?
 Perhaps it may seem necessary to store a large number of primes in order to sieve, but in fact we can easily generate all primes less than B through applying the Sieve of Eratosthenes:
@@
 	\\1. Declare p to be prime, and cross off all the multiples of that number in the table, starting from $p^{2}$;
-\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1. (O’Niel)
+	\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1.
+	\\\\Although simple, it is sufficient enough in generating the necessary amount of primes needed. Further implementation details are explained in Sect. 4.5.II Building Factor Base.
 	\\\\Now, the problem is, how do we find the necessary amount of B-smooth numbers needed to factor N?
@@
 Indeed, this approach would be much too slow, given a sufficiently large bound B, B-smooth numbers are far and few between.
-It would be a huge waste of time and resources.
-\\A further improvement could be to only consider numbers which are multiples of primes in the factor base.
+	\\\indent A further improvement could be to only consider numbers which are multiples of primes in the factor base.
 Say in our interval $[\sqrt{N},N]$ and a prime in our factor base, p, we notice that at some point, x, the number $x^{2}-N$ will be a multiple of p, which can be represented as $\sqrt{N}+i$, where i is the distance from the start of the interval.
@@
 	\\\\
-Additionally, with a defined bound B, should we consider all the primes less than B? Recall the definition of a quadratic residue:
+	Additionally, with a defined bound B, we must ask ourselves if we should even consider all the primes less than B? Recall the definition of a quadratic residue:
 	\\\\
@@
 More specifically, only those primes, $p_i$, less than $B$ such that $N$ is a quadratic residue modulo $p_i$, should be added to our factor base.
-\\Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:
+	\\\indent Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:
 	\\\\
@@
 	\\\\
-$\frac{a}{p} = $
-\\$1$ if a is a quadratic residue modulo p and $a\not\equiv 0(mod p)$
-\\$-1$ if a is quadratic non-residue modulo p
-\\$0$ if $a\equiv 0(mod p)$
-\\\\Additionally we will introduce the Law of Quadratic Reciprocity:
-\\\\
-Definition: If p and q are distinct odd primes then:
-\\(a)$(\frac{p}{q})(\frac{q}{p}) = (-1)^{\frac{(p-1)(q-1)}{4}}$
-\\(b)$\frac{1}{p} = 1$
-\\(c)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
-\\(d)$(\frac{2}{p} = (-1)^{\frac{p^{2}-1}{8}})$
+	\[
+	\frac{a}{p} = \left\{\begin{array}{lr}
+	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0$\left(mod p\right)$}\\
+	-1, & \textmd{If a is a quadratic non-residue mod p}\\
+	0, & \textmd{If $a\equiv 0\left(p\right)$}\\
+	\end{array}\right\}
+	\]
+	\\\\Additionally we will introduce the Law of Quadratic Reciprocity as defined by Gauss:
+	\\\\Definition: If p and q are distinct odd primes then:
+	\\$\left(\frac{p}{q}\right) = \left(\frac{q}{p}\right)$ if $q\equiv 1(mod 4)$ or $\left(-\frac{q}{p}\right)$ if $q\equiv 3(mod 4)$
+	\\This can be restated as $\left(\frac{p}{q}\right)\left(\frac{q}{p}\right) = \left(-1\right)^{\frac{\left((p-1)(q-1)\right)}{4}}$
+	\\\\Furthermore, these supplementary properties proved to be useful:
+	\\(a)$\frac{1}{p} = 1$
+	\\(b)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
+	\\(c)$(\frac{2}{p}) = (-1)^{\frac{p^{2}-1}{8}})$
+	\\(d)$(\frac{a}{p}) \equiv \frac{a(mod p)}{p}$
 	\\\\
@@
 
-From now, we know two ways to test whether $n$ is a quadratic residue mod p, one is Euler Criterion, and the other is Legendre symbol.
-In practice, probably because we factor base is not insanely large, we did not noticed how much faster does Legendre symbol than the Euler criterion (since Euler criterion is an $\mathcal{O}(\log{n}) $ algorithm).
+	From now, we know two ways to test whether $n$ is a quadratic residue mod p, one is Euler's Criterion, and the other is utilizing the Law of Quadratic Reciprocity.
+In practice, probably because our factor base is not insanely large, we did not notice how much faster the Law of Quadratic Reciprocity was than through Euler's Criterion (since Euler's Criterion is an $\mathcal{O}(\log{n}) $ algorithm).
 
-\subsubsection{Shanks Tonelli's Algorithm}
+	\subsubsection{Shanks-Tonelli's Algorithm}
 
-Shanks Tonelli's Algorithm is a faster algorithm to find the root of a quadratic residue.
-In class, we only learn the simple case, which is when $p \equiv 3 \pmod{4}$.
+	Shanks-Tonelli's Algorithm is a faster algorithm to find the root of a quadratic residue.
+In class, we only learned the simple case, which is when $p \equiv 3 \pmod{4}$.
 Since this algorithm is very important for quadratic sieve, we are going to prove the algorithm.
@@
 
-let $p-1 = 2^eS,\ x \equiv n^{\frac{S+1}{2}} \pmod{p},\ t \equiv n^S \pmod{p}.$
+	Let $p-1 = 2^eS,\ x \equiv n^{\frac{S+1}{2}} \pmod{p},\ t \equiv n^S \pmod{p}.$
 
-we have, $x^2 \equiv n^{S+1} \equiv n^Sn \equiv tn \pmod{p}$, notice that,
+	We have, $x^2 \equiv n^{S+1} \equiv n^Sn \equiv tn \pmod{p}$, notice that,
 
@@
 
-if $t \not\equiv 1 \pmod{p}$, then find a quadratic non-residue $a$ and let $b \equiv a^S \pmod{p}$, then, $b^{2^e} \equiv (a^S)^{2^e} \equiv a^{2^eS} \equiv a^{p-1} \equiv 1 \pmod{p}$, Since we know $a$ is a quadratic non-residue, By Euler Criterion, $a^{\frac{p-1}{2}} \equiv b^{2^{e-1}} \equiv -1 \pmod{p} \rightarrow 2^e$ is the order of b.
+	If $t \not\equiv 1 \pmod{p}$, then find a quadratic non-residue $a$ and let $b \equiv a^S \pmod{p}$, then, $b^{2^e} \equiv (a^S)^{2^e} \equiv a^{2^eS} \equiv a^{p-1} \equiv 1 \pmod{p}$, Since we know $a$ is a quadratic non-residue, By Euler Criterion, $a^{\frac{p-1}{2}} \equiv b^{2^{e-1}} \equiv -1 \pmod{p} \rightarrow 2^e$ is the order of b.
 
-we have $t^{2^e} \equiv 1 \pmod{p}$, and we let $2^{e^\prime}$ be the order of $t \pmod{p}$, since $n$ is a quadratic residue, $e^\prime \le e-1$
+	We have $t^{2^e} \equiv 1 \pmod{p}$, and we let $2^{e^\prime}$ be the order of $t \pmod{p}$, since $n$ is a quadratic residue, $e^\prime \le e-1$
 
-let $c \equiv b^{2^{e-e^\prime-1}} \pmod{p}$, $b^\prime \equiv c^2$, $t^\prime = tb^\prime$, $x^\prime = cx$, after this construction, $x^{\prime 2} \equiv t^\prime n \pmod{p}$ still holds, since $x^{\prime 2} \equiv b^{2^{e-e^\prime}}x^2 \equiv tnb^{2^{e-e^\prime}} \equiv tnb^\prime \equiv  t^\prime n \pmod{p}$.
-And we can repeat this process until $e^\prime = 0$ we can find a $t^\prime = 1$, and our final solution is $ \pm x^\prime \pmod{p}$
+	Let $c \equiv b^{2^{e-e^\prime-1}} \pmod{p}$, $b^\prime \equiv c^2$, $t^\prime = tb^\prime$, $x^\prime = cx$, after this construction, $x^{\prime 2} \equiv t^\prime n \pmod{p}$ still holds, since $x^{\prime 2} \equiv b^{2^{e-e^\prime}}x^2 \equiv tnb^{2^{e-e^\prime}} \equiv tnb^\prime \equiv  t^\prime n \pmod{p}$.
+Finally, we can repeat this process until $e^\prime = 0$ we can find a $t^\prime = 1$, and our final solution is $ \pm x^\prime \pmod{p}$
 
@@
 
-Logarithm approximation plays a very import role in implementing the sieving process.
-Since we use the polynomial $Q(x) = (x)^2-n$, and we want to sieving in the interval  $[\lfloor \sqrt{n} \rfloor - M, \lfloor \sqrt{n} \rfloor + M]$, therefore, $\log{(Q(x))} \approx \log{(Q(\lfloor \sqrt{n} \rfloor + M))} = \log{(2M\sqrt{n}+M^2)}$, because of $M^2$ is trivial if $\sqrt{n}$ is huge, $\log{(Q(x))} \approx 0.5\log{n} + log{M}$.
+	Logarithm approximation also plays a very important role in implementing the sieving process.
+	Since we use the polynomial $Q(x) = (x)^2-n$, and we want to sieve in the interval  $[\lfloor \sqrt{n} \rfloor - M, \lfloor \sqrt{n} \rfloor + M]$, therefore, $\log{(Q(x))} \approx \log{(Q(\lfloor \sqrt{n} \rfloor + M))} = \log{(2M\sqrt{n}+M^2)}$, because of $M^2$ is trivial if $\sqrt{n}$ is huge, $\log{(Q(x))} \approx 0.5\log{n} + log{M}$.
 We also know $Q(x) = \prod_{i=1}^k{p_i^{a_i}}$ where $p_i \in S_{fb}, k=|S_{fb}|$ if $Q(x)$ has a smooth relationship in our factor base, then we have,  $\log{(Q(x))} = \log{\prod_{i=1}^k{p_i^{a_i}}} = \sum_{i=1}^k{a_i\log{p_i}}$.
-This formula tell us if we can find a $\log{Q(x)} = \sum_{i=1}^k{a_i\log{p_i}} \approx 0.5\log{n} + log{M}$ it probably a candidates of smooth number.
+This formula tells us if we can find a $\log{Q(x)} = \sum_{i=1}^k{a_i\log{p_i}} \approx 0.5\log{n} + log{M}$ it is probably a good candidate to be a B-smooth number.
 
@@
 
-Quadratic Sieve's sieving method is inspired by the ancient Eratosthenes Sieve.
-The Eratosthenes sieve is to crossing out the multiples of prime, and the leftovers are the candidates of prime.
+	Quadratic Sieve's sieving method is inspired by the ancient Sieve of Eratosthenes.
+The Eratosthenes' sieve is again, to essentially cross out the multiples of primes, in which the leftover, unmarked numbers will be candidates for primes.
 In quadratic sieve, we want a relation $x^2 \equiv n \equiv r \pmod{p}$ where $r < p$, in order to keep this relation, we marking the multiples of $p$ plus $r$ as our candidates.
@@
 
-Before sieving we need to build our factor base, and in order to build our factor base, we need to choose a number $B$ which all the prime in our factor base must less than or equal to $B$.
-If $B$ is too small, it will be very hard to find such smooth relations, but if $B$ is too large, we will be facing a huge matrix and finding the null space of it will be very time consuming.
-And our $B$ choice is one million (we will explain why later).
-After choose $B$, we have another criteria for our factor base, that is the prime factor $p$ in our factor base must make our N(the number we want to factorize) to be a quadratic residue.
+	Before sieving we need to build our factor base, and in order to build our factor base, we need to choose a number $B$ in which all the primes in our factor base must be less than or equal to $B$.
+We come to a situation where if we choose a $B$ that is too small, it will be very hard to find such smooth relations, but if we choose a $B$ that is too large, we will be facing a huge matrix and finding the null space of it will be very time consuming.
+Eventually, we settled on a bound $B$ of 1,000,000 (we will explain why later).
+Again, after we choose $B$, we need to satisfy the criteria for our factor base:the prime factor $p$ in our factor base must make our N, the number we want to factor, a quadratic residue.
 
@@
 
-For each prime factor in factor base, we use shank-tonelli's algorithm to find the roots(which means the x) of $x^2 \equiv N \pmod{p}$, if $p = 2$, the root can only be 1, and for every other odd prime factor we have two roots which is $x$ and $p-x$, we save the position of $x+i*p$ and $p-x+i*p$ where $i \in \{0, 1, \dots \}$ until $x+i*p>M$ where $M$ is our bound of searching space.
-And at the meantime, accumulate $\log{p}$ to the position in our sieve array.
+	For each prime factor in factor base, we use Shanks-Tonelli's algorithm to find the roots(which means the x) of $x^2 \equiv N \pmod{p}$, if $p = 2$, the root can only be 1, and for every other odd prime factor we have two roots which is $x$ and $p-x$.
+We then proceed to continually record the positions of $x+i*p$ and $p-x+i*p$ where $i \in \{0, 1, \dots \}$ until $x+i*p>M$ where $M$ is the bound of our search space.
+In the meantime, accumulate $\log{p}$ to the position in our sieve array.
 
@@
 
-During the sieving stage, when we found a position and it's value in our sieve array is close to $0.5\log{n} + log{M}$ we consider it is our smooth candidate.
-But to define what is close to, we need a threshold.
-To determine value of the threshold little articles we read mentioned about it, some of articles said that the value of this threshold is a small error.
-We made a bunch of tests, and we found when the threshold is less than 8 it seems accurate(we will explain the detail of the tests later).
-And we also found that the threshold is good to be small, because we do not need find all the smooth relations in this range, we just need to find the relation as fast as possible.
-Since if the threshold is large, we need to double check the relation, but if the threshold is small, we do not have to.
+	During the sieving stage, when we found a position in which it's value in our sieve array is close to $0.5\log{n} + log{M}$ we consider it is our smooth candidate.
+But to define what is close, we need a threshold.
+To determine the value of the threshold, there were few resources in which we read which mention a good estimate; some articles would say that the value of the threshold is a small error.
+We ran a bunch of tests, and we found when the threshold is less than 8bits it seems accurate (we will explain the detail of the tests later).
+Additionally, we found that it is good to have a small threshold, because we do not need to find all the smooth relations in this range, we just need to find the relation as fast as possible.
+If the threshold is large, we need to double check the relation, but if the threshold is small, we do not have to.
 
@@
 	If we use logarithm approximation, it is very likely to find partial relations instead of full relation.
-A full relation means the relation is exactly the smooth number.
+A full relation means the relation is exactly a B-smooth number.
 A partial relation means that there are factors out of our factor base.
-A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which have the leftover in common, the leftover will be canceled.
-In other words, if we can find two partial relations have the same leftover factors we can treat them as one full relation.
+A relation like this is also useful, since we are working over $\mathbb{F}_2$, if we can find another partial relation which has the leftover factors in common, the leftovers will be canceled.
+In other words, if we can find two partial relations which have the same leftover factors we can treat them as one full relation.
 
-After we collecting enough relations, we use them to create a exponent matrix.
+	For example,
+
+	After collecting enough relations, we use them to create a exponent matrix.
 The common way to do this, is use trial division.
-For each relation we divide out all its  prime factor in the factor base, and use the powers mod 2 to build a exponent vector.
+For each relation we divide out all its  prime factor in the factor base, and use the powers mod 2 to build an exponent vector.
 	Then, if we can find $k$ relations where $k = |S_{fb}|$, we have k exponent vectors to form a exponent matrix.
 
-Since in our approach, $|S_{fb}|\approx 40000$, we can simply use Gaussian elimination to find null space.
-But for larger matrix, something like 100000x100000 it is better to use Block Lanczos algorithm.
-By the way, the Meataxe is using Gaussian Elimination to find null space as well.
+	Since in our approach, $|S_{fb}|\approx 40000$, we can simply use Gaussian elimination to find the null space.
+For larger matrices, however, (for example, something like 100000x100000) it is better to use Block Lanczos algorithm.
+By the way, the Meataxe is using Gaussian Elimination to find the null space as well.
 
-\subsection {Details of Our implementation \& optimization}
+	\subsection {Details of Our Implementation \& Optimization}
 
@@
 		\item \textit{Choosing B \& M:} \itemgap
-\\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}.
-At first in class professor emphasis that the number is just a toy number, therefore, we are using the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$.
-And then, we use  this bound to test our number, the result is 1.4 million and the factor base size is about 50 thousands.
-But we use pollard rho found a small factor, and we reduce the original number by dividing this factor which is 809.
-And we calculate again it became 970000+, and our factor base is shrink to 40 thousands.
+		\\ We read a lot of resources and most of them suggested a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$ (the reasoning behind choosing it this way is given in an explanation appendix A of Contini's paper \cite{contini}.
+At first in class, Professor Boklan emphasized that the number is just a toy number, therefore, we decided to use the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ instead.
+We then use this bound to test our number, resulting in 1.4 million and the a factor base of size about 50 thousand.
+However, since we used Pollard Rho to find an initial small factor, 809, we reduce the original number by dividing this factor out.
+We then recalculate again, resulting in 970000+, and a smaller factor base, shrinking to 40 thousand.
 For the convenience of communication, we choose 1 million as our B.
 
-For choosing M, we do not really know any formulas or suggestions from the resources we read.
-Our M is just based our experiments.
-Our main idea is to set M is large enough, and we continuously searching until, we found enough relations.
+		For choosing M, our search space, we did not really know of any formulas or read of any suggestions from the resources we read.
+Our M is just based on experimentation.
+Our main idea is to set M to be large enough, in which we then proceed to continuously search until, we find enough relations.
 In our experiment we set M to 2 trillion, which means we are searching 4 trillion numbers.
@@
 		\item \textit{Building Factor Base:} \itemgap
-\\ To build the factor base, first we need to generate primes.
-There are several ways to do it.
-Our approach build a prime generator by Eratosthenes Sieve.
-we used a dictionary to dynamically hold the relations.
-For example, if a test number, is not in the dictionary then it is a prime, and then add the square of this number to the dictionary.
-if the test number in the dictionary, then, pull out all its factors and add the sum of the test number and its factor to the dictionary.
-after that, delete the test number from the dictionary.
-Then, we use this generator to build our factor base, if the prime build by generator satisfy two conditions which are less than $B$ and makes $N$ be the quadratic residue, then add it to our factor base, otherwise, continue generating until the prime greater than our $B$.
-The good part of this method is that the building process is very fast, the cons is that it use extra memory to save the relations.
+		\\ To build the factor base, we first need to generate primes.
+There are several ways to do so.
+Our approach was to build a prime generator by Eratosthenes' Sieve, using a dictionary to dynamically hold the relations.
+For example, if a test number is not in the dictionary, then it is a prime, in which we then add the square of this number to the dictionary.
+If the test number is in the dictionary, then, pull out all its factors and add the sum of the test number and its factors to the dictionary.
+After that, delete the test numbers from the dictionary.
+We use this generator to build our factor base, if the prime generated by the generator satisfies two conditions: (1)the prime is less than $B$ and (2) the prime makes $N$ a quadratic residue, then add it to our factor base.
+Otherwise, continue generating until the prime greater than our $B$.
+What makes this method great is that the building process is very fast.
+However, the con is that it uses extra memory to save the relations.
 
@@
 		\\ In this stage, we did a lot optimizations.
-First, we use array as dictionary, which means we use prime value as array's index, since our B is one million, our array length is one million.
-The reason why we do this is we need extremely fast in our sieving process, since array get operation is $\mathcal{O}(1)$.
-And the downside is obviously wasting memory.
-Then, we use this approach to save 3 informations.
+First, we use an array as dictionary, which means we use prime valuse as the indices to the array, meaning since our B is one million, our array length is also one million.
+The reason why we do this is because we to be extremely fast in our sieving process.
+Since the array get operation is $\mathcal{O}(1)$ this is very fast.
+The downside, however, is obviously wasting memory.
+We then use this approach to save 3 informations.
 First one, is the roots of quadratic residue.
-Since every odd prime has two solutions, we use a two dimension array to save both.
-And we also cache the value of $\log p$, Since we do not want any unnecessary calculations in our sieving process.
-And finally, we also store the offset of x from the start position $\lfloor \sqrt{N} \rfloor - M$, i did not see any resources mentioned this, but we think it is useful, since we can very easily obtain the smooth number by just add offset to start position.
+Since every odd prime has two solutions, we use a two dimensional array to save both.
+Secondly, we also cache the value of $\log p$, since we do not want any unnecessary calculations in our sieving process.
+Finally, we also store the offset of x from the start position $\lfloor \sqrt{N} \rfloor - M$.
+We did not see any resource mention this, but we think it is useful, since we can very easily obtain the smooth numbers by just adding the offset to the starting position.
 
-And here is a story about how math help us solve problems.
-As we motioned before, we want save the info of the offset of x from the start position, which is also find the closest position from x that satisfy $x+o \equiv r \pmod{p}$ where $x$ is start position $o$ is offset, and $r$ is the square roots of quadratic residue.
-And we want find $o$, at very first we use a very naive way to do it, since $x+o=r+ip$ where $i \in \{0,1,\dots\}$ we just keep increasing i until we found a value makes two side equal.
-And then we found this approach was very slow when the factor base is getting bigger (we used to choose a much smaller factor base).
-Then, we just sit down and wrote down the formula and analysis.
-And we realize if we want the $o$, it is just simply $o = r-x \pmod{p}$.
-After we use this new approach the program runs 2 times faster than before.
-Then we think, do a math analysis before writing code is probably a good idea.
+		Here is a story about how math helped us solve problems.
+As we mentioned before, we wanted to save the info of the offset of x from the start position, which is also to find the closest position from x that satisfies $x+o \equiv r \pmod{p}$ where $x$ is start position $o$ is offset, and $r$ is the square roots of quadratic residue.
+We also want to find $o$, at the very beginning we used a very naive way to do it.
+Since $x+o=r+ip$ where $i \in \{0,1,\dots\}$ we just kept increasing i until we found a value which made both two sides equal.
+We found that this approach became very slow when the factor base gets larger(we used to choose a much smaller factor base), but after much analysis we realize that if we want the $o$, it is just simply $o = r-x \pmod{p}$.
+After we implement this new approach the program runs 2 times faster than before.
+So the moral of the story is, doing a mathematical analysis before writing code is probably a good idea.
 
@@
 
+	\section {Collecting data by parallel computing} 
+	\subsection{Computer spec}
+	computer 1: i7-4700M, 2.4GHz (boost 3.1Ghz), RAM 16G\\
+	\indent computer 2: i7-3537U, 2.0GHz               , RAM 8G\\
+	\indent computer 3: i5-3570K, 3.4GHz               , RAM 16G\\
+	\indent computer 4: i5-4210U, 1.7GHz               , RAM 8G
+
+	\subsection{Data collection}
+	We collect 706854 relations in 3 hours and 20 minutes with 4 parallel computing computers.
+In the 706854 relations, there are 48059 full relations, 305914 partial relations and the remaining are duplicate relations.
+	Thus, there are about 85$\%$ of the relations are partial relations. In other words, when modulus N grows bigger and bigger, the probabilities of finding full relations gets lower and lower.
+
 	\section {Decoding the message}
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\textwidth]{tree.png}
-\end{figure}
-
 		and we use this little program to list all possibilities to give us hints.
@@
 
-And finally, we solve this assignment.
+	And finally, we solve this assignment and decrypt message M shown as following:\\
+
+	1 12 12 25 15 21 7 15 20 20 15 4 15 9 19 20 18 25 20 18 25 1 12 9 20 20 12 \\
+	\indent 5 20 5 14 4 5 18 14 5 19 19\\
+
+	all you got to do is try try a little tenderness
 
@@
 		\bibitem{pomerance} Pomerance, [\textit{Smooth Numbers and the Quadratic Sieve }], Algorithmic Number theory MIRI Publication Volume 44, 2008
+
 		\bibitem{williams} H.C. Williams, [\textit{A p+1 Method of Factoring}], Mathematics of computation volume 39, Number, 159 July 1982
+
+		\bibitem{charest} Annie-Sophie Charest, [\textit{Pollard's p-1 and Lenstra's factoring algorithms}], Oct.2,2005
 

### 2016-11-29 Paper/Paper.tex
updated tree.png
update cases

@@
 
-	\section{The Quadratic Sieve}
-	At last, we had reached the conclusion that we may have to implement the Quadratic Sieve in order to factor our N.
-According to Carl Pomerance, the mind behind the Quadratic Sieve, the Quadratic Sieve is the fastest for numbers under 100 digits\cite{pomerance}.
-This method was created after a series of enhancements on Fermat's factoring method utilizing smooth numbers, and matrices of exponent vectors in order to assure that such a square needed for Fermat's method would be found.
-We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
-	\\\\
-	Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works.
-We will then explain our our task of implementing the Quadratic Sieve, as well as the problems that we were faced with.
-	\subsection{Basic's of the Algorithm}
-
-	\subsection{Application of Linear Algebra}
-	\indent For In this section we will talk about the input of Linear Algebra for this algorithm.
-All information in this section not within "A Tale of Two Sieves" will be otherwise sourced.
-Linear Algebra is a key component to the quadratic Sieve Algorithm and is the tool used to actually identify the numbers that would be factors out of all the potential candidates found in the data collection/Sieving phase.
-This component of the Quadratic Sieve method was created when John Brillheart and Michael Morris Utilization multiple linear algebra concepts we convert the smooth numbers found in the earlier stages of the algorithm into exponent vectors.
-As in a vector of the exponents of a numbers prime factors.
-This vector shall be converted into a vector in a finite field of size 2 ($F_2$).
-This is due to the fact that a number is a square if and only if all of it's prime factors exponents add up to zero.
-Thus there is no need to have the vectors number be out of $F_2$.
-The objective of having these vectors is to create a matrix of theses exponent vectors.
-The size of the matrix will be the size of our factor base cross the size of our factor base plus at least 1,(so if $F_B = p_0p_1\dots p_i$ we will have a matrix of size $(ixi)+1$) With this matrix we will use a few properties of linear algebra to find which combination of smooth numbers will give us our factorization.
-	\\\\
-	\indent So firstly, why do we add the vectors?
-This is because adding the vectors is the equivalent of multiplying the integers themselves in terms of determining if the product of those two numbers (or more) will be a square.
-As an example consider the integers $24 = 2^{3}*3^{1}$ and $15 = 3^{1}*5^{1} $ The exponent vectors for these two will be 110 and 011 the sum vector of these two numbers is not zero and hence the multiple of 24 and 15 is not a square.
-Secondly the reasoning to having one more vector than the size of the factor is due to a linear algebra concept known as Linear dependence.
-Linear dependence tells us that when the number of vectors(rows) exceed the number of dimensions (columns), the sum of a subset of the vectors must be equal to zero.
-Now finding the subset of vectors that equal to zero can be computationally difficult if the matrix became large enough (if you simply try all the combinations ), however there is a technique within Linear Algebra called Gaussian Elimination that can greatly decrease the complexity of finding the zero subset (discussed more in the implementation section).
-Thus by ensuring that the amount of smooth numbers collected exceeds the factor base guarantees that we obtain a square within the resulting matrix.
-Obtaining a factor from the square is not guaranteed however, as half of the possible squares will yield an uninteresting solution.
-So even with the convenience of the matrix there is some luck involved.
-
 	\section{Quadratic Sieve}
@@
 	\\\\
-	\[
-	\frac{a}{p} = \left\{\begin{array}{lr}
-	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0$\left(mod p\right)$}\\
-	-1, & \textmd{If a is a quadratic non-residue mod p}\\
-	0, & \textmd{If $a\equiv 0\left(p\right)$}\\
-	\end{array}\right\}
-	\]
+	$$
+	\frac{a}{p} = \begin{cases}
+	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0 $\pmod{p}$}\\
+	-1, & \textmd{If a is a quadratic non-residue $\pmod{p}$}\\
+	0, & \textmd{If $a\equiv 0 \pmod{p}$}\\
+	\end{cases}
+	$$
 	\\\\Additionally we will introduce the Law of Quadratic Reciprocity as defined by Gauss:
@@
 
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=0.6\textwidth]{tree.png}
+		\end{figure}
+
 		\pagebreak

### 2016-11-29 Paper/Paper.tex
akeem p+1

@@
 The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had.
-When actually run on the original modulus the algorithm once again found 809 to be a factor about 5 seconds.
-Use of the method on the modulus with 809 divided out produced no further results, even when run for over 20+ hours.
-At this time an estimate for the time the program would actually factor the second modulus has not been produced.
-The only new information that could be extrapolated from this would be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed.
+The use of the P+1 method on 50 bit integers produce the factors in an average .0125 to .015 (there were a few outliers that took up to 5-10 seconds however) At around 100 bits the method takes around .5 to .8 seconds to produce a factor.
+When actually run on the original modulus the algorithm once again found 809 to be a factor in an average time of about .018 to .021 seconds.Despite the results on even some numbers in the 200 bit range(average run time of 2 to 5 seconds)  use on the modulus with 809 divided out produced no further results, even when run for over 20+ hours.
+The only new information that could be extrapolated from this could be that the probability of the p+1 of the larger number being comprised of mostly small factors would be low provided that the premise of the algorithm itself is to be believed.
 This ends the discussion of William's P+1 method and our attempt to implement it for our assignment.

### 2016-11-29 Paper/Paper.tex
Profread

--- 2016-11-29 Paper/Paper.tex
@@
 
-	Quadratic Sieve method is actually built upon previous factorization method.
+	Quadratic Sieve method is actually built upon a previous factorization method.
 It is a optimization of Dixon's Factorization Method.
@@
 
-	For example,
-
 	After collecting enough relations, we use them to create a exponent matrix.
@@
 At first in class, Professor Boklan emphasized that the number is just a toy number, therefore, we decided to use the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ instead.
-We then use this bound to test our number, resulting in 1.4 million and the a factor base of size about 50 thousand.
+We then use this bound to test our number, resulting in B being 1.4 million and the a factor base of size about 50 thousand.
 However, since we used Pollard Rho to find an initial small factor, 809, we reduce the original number by dividing this factor out.
-We then recalculate again, resulting in 970000+, and a smaller factor base, shrinking to 40 thousand.
+We then recalculate again, resulting in B of 970000+, and a smaller factor base, shrinking to 40 thousand.
 For the convenience of communication, we choose 1 million as our B.
@@
 
-		To decide whether $\legendre{N}{p} = 1$, we implemented both Euler criterion and Legendre Symbol.
-And probably because our factor base was not enough, we did not notice Legendre Symbol is much faster than Euler Criterion.
-Since professor suggest us use Legendre Symbol, we are using Legendre symbol to test $\legendre{N}{p}$.
+		Again, to decide whether $\legendre{N}{p} = 1$, we implemented both Euler's Criterion and Legendre Symbol and again probably because our factor base was not that large, we did not notice that much of a difference in the Law of Quadratic Reciprocity over Euler's Criterion.
+Since Professor Boklan, suggested us to use Law of Quadratic Reciprocity, we ended up using this to test $\legendre{N}{p}$.
 
@@
 		\\ In this stage, we did a lot optimizations.
-First, we use an array as dictionary, which means we use prime valuse as the indices to the array, meaning since our B is one million, our array length is also one million.
+First, we use an array as a dictionary, which means we use prime valuse as the indices to the array, meaning since our B is one million, our array length is also one million.
 The reason why we do this is because we to be extremely fast in our sieving process.
@@
 		\item \textit{Sieving:} \itemgap
-		\\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$].
+		\\ The sieving array is used to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$].
 Therefore, its length is $2M+1$.
-The sieving process is just go through each prime in our factor base.
-Get its position which already cached in previous stage, and add $r+ip$ where $r$ is the position to the sieve array.
+The sieving process goes as follows:\\(1) For each prime in our factor base, $p$, get its position which should already be cached in the pre-sieving stage\\(2) Add $r+ip$ where $r$ is the position in the sieve array for $i\ge0$ but $r+ip<M$.
 
-		This stage is probably most simple part of our program.
-It is not the idea is simple, it is made to be simple, since this is the bottle neck of our whole program.
-if we made this process calculates more, the program will slow down dramatically.
-And we also did this part in parallel.
-Not only multi-thread but also multi-process.
+		This stage is probably the most simple part of our program.
+However, it is not the idea that is simple, but it was made to be simple, since this is the bottle neck of our whole program.
+If we made this process calculate more, the program will slow down dramatically.
+Additionally, we did this part in parallel, utilizing multi-threading but also multi-processing.
 
-		We implemented a sever which only responsible to generate job which specify the range to search and add it to a task queue.
-And then, each client connected to sever and got job from the queue.
-The job could be very large, so we split the job according to the memory of client, and starting multiple threads according to the number of processors of client.
-Then, each thread search different ranges within the job.
+		We implemented a server whose sole responsible was to generate jobs.
+Each job specifies the range in which we search for smooth candidates.
+Each job is then added to a task queue in which each client who is connected to server will take a job off the queue.
+Additionally, the jobs can be very large, so we split the jobs according to the memory of the client; starting multiple threads according to the number of processors the client has in which each thread searches a different range within the job.
 
 		\item \textit{Save Sieving Result:} \itemgap
-		\\ If we found a relation $\left|sieve\_array[position]-(0.5\log{N}+\log{M})\right| < threshold$ during the sieving, we consider this position is our smooth candidate, and save this position to our candidates set.
-And the reason we use the data structure of set is that it is possible to have duplicate positions and we want avoid checking process.
-We know for a set to check inclusion is very fast, since it just check whether the hash of target is in the table, which is almost $\mathcal{O}(1)$.
+		\\ If we found a relation $\left|sieve\_array[position]-(0.5\log{N}+\log{M})\right| < threshold$ during the sieving, we consider this position a smooth candidate, and save this position to our candidates set.
+The reason we use the set data structure is that it is possible to have duplicate positions and we want to avoid a checking process to remove those duplicates.
+We know that for sets, to check inclusion is very fast, since it is just to check whether the hash of target is in the table, which is almost $\mathcal{O}(1)$.
 
 		When finish sieving, we go through each position we saved, and do trial division.
-We  only record the full relations, and the partial relations with prime leftover.
-And we use millar rabin testing check the primality of the leftover.
+We only record the full relations, and the partial relations with primes leftover.
+In order to check for the primality of the leftover primes, we use Millar-Rabin primality testing.
 
-		And we also record the odd power prime factors, and save these informations to a concurrent set.
-Since this process will do in parallel, we have to keep in mind that concurrency would be a issue, therefore, we need to keep mutual exclusive when we do the save action.
+		In addition, we need to record the odd power prime factors, and save this information to a concurrent set.
+Since this process will be done in parallel, we have to keep in mind that concurrency would be a issue, therefore, we need to keep mutual exclusiveness when we do the saving action.
 
-		After collecting all the data, the client will sent it back to sever. And sever just simply save them in a file.
+		After collecting all the data, the client will send it back to server, which the server then simply saves in a file.
 
 		\item \textit{Build Exponent Matrix:} \itemgap
-		\\ We retrieve the file from sever, and parse it line by line.
-Here we met a problem that still confused us that is even though we collect data in different range , we find duplicates relations.
-This problem force us to collect more relations than we need.
-It could be a bug of our code.
-So, we need check duplication first.
-		After that since each line in file correspond to a relation, we need to differentiate full or partial relations.
-if it is full relation we just save $x$ in a list and all the prime factors of $Q(x)$ in a dictionary, prime factor as key, and exponent as value.(why we save this will be explained in \textit{Calculating Factors}).
-Since we have the odd exponent factors information of the relation, it is very simple to use it building a exponent vector and save it in matrix.
-if it is partial relation, we save it a dictionary first, and use the leftover as a key.
-until we find another partial relation have the same leftover, we pop out it from the dictionary, and combine two relation together as following.
+		\\ We retrieve the file from server, and parse it line by line.
+Here we faced a problem that still confuses us; even though we collect data in different ranges, we still found duplicate relations, though the reason behind these duplicates could just be a bug in the code.
+This problem forced us to collect more relations than we need which we then had to be wary of duplicates when parsing.
+		Afterwards, since each line in the file corresponds to a relation, we need to differentiate full or partial relations.
+If it is full relation we just save $x$ in a list and all the prime factors of $Q(x)$ in a dictionary: using a prime factor as key, and exponent as value.(why we saved them this will be explained in \textit{Calculating Factors}).
+Since we have information on the odd exponent factors of the relation, it is very simple to use it building a exponent vector and save it in the matrix.
+If it is partial relation, we save it to a dictionary first, and use the leftover as a key.
+Until we find another partial relation(having the same leftover), we pop it from the dictionary, and combine the two relations together as follows.
 First, we multiply $x_1$ and $x_2$ as $x$, then, merge the two prime factor dictionaries.
-Finally, we xor two exponent vectors and save it in matrix.
+Finally, we xor the two exponent vectors and save it in the matrix.
 
-		Since we did not use the meataxe, we need introduce our matrix implementation.
-The reason why we were not using meataxe is that it is not very well documented, and sometimes it does not work as we expected.
-We are afraid of spending too many time on it.
-And another reason is our number is not insanely large, it just 40000x40000 matrix.
+		Since we did not use the meataxe, we need to introduce our matrix implementation.
+The reason why we did not using meataxe is that it is not very well documented, and sometimes it does not work as we expected.
+We were afraid of spending too much time on it, and seeing that our 40000x40000 matrix is not insanely large.
 
-		And the reason why it is hard to manipulate large matrix is our ram not big enough to save it.
+		The reason why it is hard to manipulate large matrices is because our RAM is not large enough to save it.
 Let us do a simple calculation, 40000x40000=1600000000 elements.
 If we use a integer to represent each element that will cost 1600000000*4=6400000000 bytes $\approx$ 6Gb ram.
-This is too memory consuming.
-However, since the matrix is over $\mathcal{F}_2$, we can use binary representation for each element it will only cost 6Gb/32 $\approx$ 190Mb which is acceptable.
+This is too large of a memory consumption.
+However, notice since the matrix is over $\mathcal{F}_2$, we can use binary representation for each element it will only cost 6Gb/32 $\approx$ 190Mb which is acceptable.
 
@@
 
-		First, we make a very simple header, which only has two integers that specific the row number and the column number.
+		First, we make a very simple header, which only has two integers that specific the number of rows and columns.
 Then, we use 1 byte to represent 8 bits, and if the matrix's column size mod 8 is not 0, we are padding zeros after each row.
@@
 This is for sake of simplicity of implementation.
-And finally, we just save each row linearly.
+Finally, we just save each row linearly.
 
-		To access certain rows, say the 8th row, we have our initial position pointer $s$, and we calculate many bytes in each row by row\_length = (column+padding)/8, and the start position of 8th row is 8*row\_length+$s$.
+		To access certain rows, say the 8th row, we have our initial position pointer $s$, and we calculate how many bytes in each row, row\_length = (column+padding)/8, in which we can find the start position of 8th row, 8*row\_length+$s$.
 
-		To access certain column, say the 6th column, we calculate this column in which byte by 6/8=0, this means 6th column belongs to the first byte, then, take the byte and right shift 6 position and do a ``and'' operation with 1 which means ignore other bits except for the last bit.
+		To access certain columns, say the 6th column, we calculate in a similar way.
+A column in which byte by 6/8=0, this means 6th column belongs to the first byte, then, take the byte and right shift 6 position and do a ``and'' operation with 1 which means to ignore other bits except for the last bit.
 
@@
 The reason why we can use Gaussian elimination to find null space, is because any elementary row operation can be seen as a matrix transformation.
-For example.
+For example:
 
@@
 
-		So, if we reduce $M$ to its reduced echelon form $M^\prime$ by Gaussian Elimination, means that $\exists E=\prod_{i=1}^k{E_i}\ s.t.\ EM \rightarrow M^\prime$, where $E_i$ is the elementary row operation.
-We also know at the bottom of reduced echelon form always have all zero rows, and that is the null space.
+		So, if we reduce $M$ to its reduced echelon form $M^\prime$ by Gaussian Elimination, which means $\exists E=\prod_{i=1}^k{E_i}\ s.t.\ EM \rightarrow M^\prime$, where $E_i$ is the elementary row operation.
+We also know that at the bottom of the reduced echelon form matrix, it will always have all zero rows, which is the null space.
 
-		Our approach is to records all the elementary operation by using a identity matrix $I$ since $EI=E$.
+		Our approach is to record all the elementary operations by using a identity matrix $I$ since $EI=E$.
 
@@
 
-		First, we will going to explain why finding null space is equal to find the sum of rows equal to zero.
-It is easy only if you notice that and none of the resources we read explained this.
-It is just because the matrix production is for each row multiply a coefficient add rows together.
-And we are working over $\mathbb{F}_2$, the multiplier 0 means not using this row, 1 means using this row.
-And this is the reason why we are checking each element of the vector in null space, if we found a 1, we find the corresponding row in matrix and get related $x$ and all the prime factors of $Q(x)$.
+		First, we will explain why finding the null space is equal to finding the sum of rows equal to zero, because initially we did not realize this ourselves from all the resources we read.
+Recall the how we perform the product of the matrices: for each row multiply a coefficient add rows together.
+We are working over $\mathbb{F}_2$, the multiplier 0 means not using this row, 1 means using this row, which is why we are checking each element of the vector in the null space; if we found a 1, we find the corresponding row in matrix and get related $x$ and all the prime factors of $Q(x)$.
 
 		Recall that in \textit{Building Exponent Matrix} Section, we said we will explain why we save all the prime factors of $Q(x)$ instead of just saving $Q(x)$ itself.
-The reason is that if we multiply these $Q(x)$ , we get an insanely large number, we do not know any good algorithm to find the square root of it, we tried newton's square root approximation, which did not help us much.
-We can not get a accurate number.
-Therefore, we saved all the prime factor and their exponents.
-And then, we only need to half of the exponent and multiply them together we get the $\sqrt{\prod Q(x)}$.
+The reason is that if we multiply those $Q(x)$ , we get an insanely large number, which we do not know of any good algorithm to find the square root of.
+We tried Newton's Square Root approximation, which did not help us much, seeing as we were unable to get an accurate enough of a number.
+Therefore, we saved all the prime factors and their exponents, which we then only have to halve the exponents and multiply them together,getting $\sqrt{\prod Q(x)}$.
 
-		After we got $\sqrt{\prod Q(x)}$, our final answer is $gcd\left(\prod Q(x) \pm \prod x, N\right)$, if we are lucky not all relation we've found are trivial, we have one factor of N.
+		After we got $\sqrt{\prod Q(x)}$, our final answer is $gcd\left(\prod Q(x) \pm \prod x, N\right)$. If we are lucky and not all of the relations we find are trivial, we have finally the factors of N.
 
@@
 	\subsection{Computer spec}
-	computer 1: i7-4700M, 2.4GHz (boost 3.1Ghz), RAM 16G\\
-	\indent computer 2: i7-3537U, 2.0GHz               , RAM 8G\\
-	\indent computer 3: i5-3570K, 3.4GHz               , RAM 16G\\
-	\indent computer 4: i5-4210U, 1.7GHz               , RAM 8G
+	Computer 1: i7-4700M, 2.4GHz (overclocked to 3.1Ghz), RAM 16G\\
+	\indent Computer 2: i7-3537U, 2.0GHz               , RAM 8G\\
+	\indent Computer 3: i5-3570K, 3.4GHz               , RAM 16G\\
+	\indent Computer 4: i5-4210U, 1.7GHz               , RAM 8G
 
 	\subsection{Data collection}
-	We collect 706854 relations in 3 hours and 20 minutes with 4 parallel computing computers.
-In the 706854 relations, there are 48059 full relations, 305914 partial relations and the remaining are duplicate relations.
-	Thus, there are about 85$\%$ of the relations are partial relations. In other words, when modulus N grows bigger and bigger, the probabilities of finding full relations gets lower and lower.
+	We collect 706854 relations in 3 hours and 20 minutes with 4 computers computing in parallel.
+In the 706854 relations, there are 48059 unique full relations, and 305914 unique partial relations.
+The remaining 352,881 relations are duplicate relations.
+	Additionally, approximately 85$\%$ of the relations are partial relations. In other words, when our x grows larger and larger, the probability of finding full relations gets lower and lower.
 
@@
 
-	Once we got the factors of N, we use Euler-totient function calculates the $\varphi(N)$, and then we can calculate the private key $d$ by find the mod inverse of $e \mod{\varphi(N)}$ thorough extend euclidean gcd algorithm.
-After we got $d$ we can recover the message just by taking $(m^e)^d \pmod{n}$.
+	Once we got the factors of N, calculate the $\varphi(N)$, and then we can calculate the private key $d$ by find the mod inverse of $e \mod{\varphi(N)}$ through the Extend Euclidean Algorithm.
+After we get $d$ we can recover the message just by taking $(m^e)^d \pmod{n}$.
 
-	Then, we got a message encoded as 1121225152171520201541591920182520182511292020125\\2051445181451919.
+	Ultimately, we get a message encoded as 1121225152171520201541591920182520182511292020125\\2051445181451919.
 Since, we know it is English and the encoding method already, we use three methods to recover it to English very quickly.
@@
 	\begin{enumerate}
-		\item We use a English dictionary, and encodes the words exactly the same way as the message did.
-And we only searching for the longer words(at least 4 letters).
-And we extract the matching part, which could shrink the length of the message.
-In our case, we use this method found the word ``tenderness''.
+		\item We use an English dictionary, and encode the words exactly the same way as the message did.
+We then only search for the longer words(at least 4 letters) and we extract the matching part, which could shrink the length of the message.
+In our case, using this method, we found the word ``tenderness''.
 
 		\item We wrote a program to calculate all the possible combinations.
-The idea is using backtrack algorithm to build a tree.
-Then, saving all the leaves in the tree.
-Finally, collecting each path from the leaf to root.
+The idea is using backtrack algorithm to build a tree ,then saving all the leaves in the tree.
+Finally, we collect each path from the a leaf to the root.
 The example for code 21525 in below:
@@
 
-		\item Since the message is not very long and encoding method is easy, we just use our English knowledge to test whether the words make sense in its place.
+		\item Since the message is not very long and encoding method is easy, we just use some human intuition and English knowledge to test whether the words make sense in its place.
 
@@
 
-	And finally, we solve this assignment and decrypt message M shown as following:\\
+	Finally, with much effort, we were finally able to retrieve and decrypt the original message, M, shown as following:\\
 

### 2016-11-29 Paper/Paper.tex

@@
 The paper itself mentions in the implementation and results section that the P+1 method was about 9 times slower than the P-1 method possibly likely due to the calculation of a Lucas sequence on top of the calculation of the factorial that the P-1 method already had.
-When actually run on the original modulus the algorithm once again found 809 to be a factor about 5 seconds.
+When actually run onfthe original modulus the algorithm once again found 809 to be a factor about 5 seconds.
 Use of the method on the modulus with 809 divided out produced no further results, even when run for over 20+ hours.
@@
 		Again, to decide whether $\legendre{N}{p} = 1$, we implemented both Euler's Criterion and Legendre Symbol and again probably because our factor base was not that large, we did not notice that much of a difference in the Law of Quadratic Reciprocity over Euler's Criterion.
-Since Professor Boklan, suggested us to use Law of Quadratic Reciprocity, we ended up using this to test $\legendre{N}{p}$.
+Since Professor Boklan, suggested us to use the Law of Quadratic Reciprocity, we ended up using this to test $\legendre{N}{p}$.
 
@@
 The downside, however, is obviously wasting memory.
-We then use this approach to save 3 informations.
-First one, is the roots of quadratic residue.
+We then use this approach to save three pieces ofinformation.First one, is the roots of quadratic residue.
 Since every odd prime has two solutions, we use a two dimensional array to save both.
@@
 		First, we will explain why finding the null space is equal to finding the sum of rows equal to zero, because initially we did not realize this ourselves from all the resources we read.
-Recall the how we perform the product of the matrices: for each row multiply a coefficient add rows together.
+After finding the null space, each vector in the null space will contain coefficients in which each coefficient corresponds to a row in the original matrix.Recall we perform the product of the matrices: for each row multiply by a coefficient, and add the addows together.
 We are working over $\mathbb{F}_2$, the multiplier 0 means not using this row, 1 means using this row, which is why we are checking each element of the vector in the null space; if we found a 1, we find the corresponding row in matrix and get related $x$ and all the prime factors of $Q(x)$.
@@
 
-		\pagebreak
+		\begin{figure}[h]
+
+			\includegraphics[width=0.6\textwidth]{tree.png}
+		\end{figure}
 

### 2016-11-29 Paper/Paper.tex
idk
updates array-->cases
remove

@@
 \title{RSA Project Report Paper}
-\author{\textbf{RSA Group}\\Li Qiu\\Yiwei \\Leester Mei\\Akeem}
+\author{\textbf{RSA Group}\\Li Qiu\\Yiwei Sun\\Leester Mei\\Akeem Miller}
 %\date{} % Activate to display a given date or no date (if empty),
@@
 	\\\\
-	\[
-	\frac{a}{p} = \left\{\begin{array}{lr}
-	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0$\left(mod p\right)$}\\
-	-1, & \textmd{If a is a quadratic non-residue mod p}\\
-	0, & \textmd{If $a\equiv 0\left(p\right)$}\\
-	\end{array}\right\}
-	\]
+	$$
+	\frac{a}{p} = \begin{cases}
+	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0$\pmod{p}$}\\
+	-1, & \textmd{If a is a quadratic non-residue $\pmod{p}$}\\
+	0, & \textmd{If $a\equiv 0 \pmod{p}$}\\
+	\end{cases}
+	$$
 	\\\\Additionally we will introduce the Law of Quadratic Reciprocity as defined by Gauss:
 	\\\\Definition: If p and q are distinct odd primes then:
-	\\$\left(\frac{p}{q}\right) = \left(\frac{q}{p}\right)$ if $q\equiv 1(mod 4)$ or $\left(-\frac{q}{p}\right)$ if $q\equiv 3(mod 4)$
+	\\$\left(\frac{p}{q}\right) = \left(\frac{q}{p}\right)$ if $q\equiv 1(mod\ 4)$ or $\left(-\frac{q}{p}\right)$ if $q\equiv 3(mod\ 4)$
 	\\This can be restated as $\left(\frac{p}{q}\right)\left(\frac{q}{p}\right) = \left(-1\right)^{\frac{\left((p-1)(q-1)\right)}{4}}$
